---
title: "Estimate syndromic prevalences"
author: "Laura Grajeda"
date: "11 de mayo de 2020"
output:
  html_document:
    toc: yes
    toc_depth: 2
    df_print: paged
  pdf_document:
    keep_tex: no
    number_sections: yes
    toc: yes
    toc_depth: 2
---


```{r include=FALSE}
library(tidyverse)
library(survey)
library(compareGroups)
library(readxl)
library(here)
library(broom)
```


# 1. Objetivo

Estimate the prevalence of pneumonia, ILI, Diarrhea, and FUO. This includes

-Calculate proportions
-Calculate prevalence taking into account the weights and poststratification
-Compare the prevalence before and during the pandemic using prevalence ratios

Every calculation is done stratified by population group

# 2. Datos

```{r}
PTam <- readRDS(here("1_Create_dataset","output", "HUS_dataset.rds")) 
pop3 <- readRDS(here("1_Create_dataset","output", "Population_Totals_CensusDataset.rds")) 
```


Create numerical and factor variables for syndrome
```{r}
PTam$elegibleneumonia_num <- as.numeric(PTam$elegibleneumonia)
PTam$elegibleili_num <- as.numeric(PTam$elegibleili)
PTam$elegiblefebril_FUO_num <- as.numeric(PTam$elegiblefebril_FUO)
PTam$elegiblediarrea_num <- as.numeric(PTam$elegiblediarrea)


PTam$elegiblefebril_FUO <- factor(PTam$elegiblefebril_FUO, levels = c(1,0), labels = c("Si", "No"))
PTam$elegiblefebril7_FUO <- factor(PTam$elegiblefebril7_FUO, levels = c(1,0), labels = c("Si", "No"))
PTam$elegibleili <- factor(PTam$elegibleili, levels = c(1,0), labels = c("Si", "No"))
PTam$elegibleili7 <- factor(PTam$elegibleili7, levels = c(1,0), labels = c("Si", "No"))
PTam$elegiblediarrea <- factor(PTam$elegiblediarrea, levels = c(1,0), labels = c("Si", "No"))
PTam$elegiblediarrea7 <- factor(PTam$elegiblediarrea7, levels = c(1,0), labels = c("Si", "No"))
PTam$elegibleneumonia <- factor(PTam$elegibleneumonia, levels = c(1,0), labels = c("Si", "No"))
```

Create factor variables for period and population groups
```{r}
PTam$edad15 <- factor(PTam$edad15)
PTam$edad5 <- factor(PTam$edad5)
PTam$COVID <- factor(PTam$COVID)
PTam$COVID_num <- ifelse(PTam$COVID=="During",0,1)
```


Sociodemographic variables
```{r}
PTam |> count(hacinamiento_cat)
PTam$hacinamiento_cat <- factor(PTam$hacinamiento_cat, 
                                levels=c("<=2", "(2, 3]", ">3"),
                                labels=c("<=2", "(2, 3]", ">3"),
                                ordered = T)
PTam$hacinamiento_bin <- ifelse(PTam$hacinamiento_cat==">3",1,0)


PTam |> count(SES_Tertiles)
PTam$SES_Tertiles <- factor(PTam$SES_Tertiles, 
                                levels=c("Low", "Medium", "High"),
                                labels=c("Low", "Medium", "High"),
                                ordered = T)

PTam |> count(edadcat)
PTam$edadcat <- factor(PTam$edadcat, 
                                levels=c("00-04", "05-14", "15-44", "45-64", ">=65"),
                                labels=c("00-04", "05-14", "15-44", "45-64", ">=65"),
                                ordered = T)

PTam |> count(idiomahogar_des)
PTam$idiomahogar_des2 <- factor(ifelse(PTam$idiomahogar_des=="Spanish",1,0),
                                levels = c(1,0),
                                labels = c("Spanish", "Maya"))
PTam$idiomahogar_des <- factor(PTam$idiomahogar_des)
  
  
PTam |> count(combustiblecocinaprincipal_cal)
PTam$combustiblecocinaprincipal_cal <- factor(PTam$combustiblecocinaprincipal_cal)

PTam |> count(fuenteagua_cal)
PTam$fuenteagua_cal <- factor(PTam$fuenteagua_cal)

PTam |> count(sanitario_cal)
PTam$sanitario_cal <- factor(PTam$sanitario_cal)

PTam |> count(sexo_des)
PTam$sexo_des <- factor(PTam$sexo_des)
```


```{r}
PTam |> count(Period)
```


# 3. Proportions

## BEFORE COVID

Solo incluir el periodo que no esta afectado por COVID. Este periodo tiene personas de todas las edades. 

## + By edad5
```{r}
Prev <-compareGroups(edad5 ~ elegibleneumonia + 
                     elegibleili + elegibleili7 +
                     elegiblefebril_FUO + elegiblefebril7_FUO + 
                     elegiblediarrea + elegiblediarrea7,
                     # solo incluye datos PRE-COVID  
                     data=PTam %>% filter(Period=="Before COVID - All ages"),
                     method = c(edad=2),
                     include.label = T)

dt<-createTable(Prev, digits = 0, show.n = T, show.all = T)
print(dt, header.labels = c(all = "Prevalencias"), which.table = "both")
export2xls(dt, file= "output/Proportions_Before COVID by age group.xlsx", header.labels = c(all = "Elegibles"), which.table = "both")
```

  
## + By sex
```{r}
Prev <-compareGroups(sexo_des ~ elegibleneumonia + 
                     elegibleili + elegibleili7 +
                     elegiblefebril_FUO + elegiblefebril7_FUO + 
                     elegiblediarrea + elegiblediarrea7,
                     # solo incluye datos PRE-COVID  
                     data=PTam %>% filter(Period=="Before COVID - All ages"),
                     method = c(edad=2),
                     include.label = T)

dt<-createTable(Prev, digits = 0, show.n = T, show.all = T)
print(dt, header.labels = c(all = "Prevalencias"), which.table = "both")
#export2xls(dt, file= "output/Proportions_Before COVID by sex group.xlsx", header.labels = c(all = "Elegibles"), which.table = "both")
```


## BEFORE AND DURING COVID

Solo incluye individuos <15 anos y quita periodo during covid de AMR. En este periodo se excluyeron hogares y personas por tener COVID, es decir se exclueron personas que podrian ser positivas para algun sindrome. Este periodo tambien incluye meses diferentes y esto podria dar dudas sobre la comparabilidad.
                    
## + Overall 
```{r}
Prev <-compareGroups(COVID ~ elegibleneumonia + 
                    elegibleili + elegibleili7 +
                    elegiblefebril_FUO + elegiblefebril7_FUO + 
                    elegiblediarrea + elegiblediarrea7,
                    # Solo incluye individuos <15 anos y quita periodo during covid de AMR. 
                    # En este periodo se excluyeron hogares y personas por tener COVID, 
                    # es decir se exclueron personas que podrian ser positivas para algun sindrome.
                    # Este periodo tambien incluye meses diferentes y esto podria dar dudas sobre la comparabilidad.
                    data=PTam %>% filter(Period!="During COVID - All ages" & edad15=="Menor15"),
                    method = c(edad=2),
                    include.label = T)

dt<-createTable(Prev, digits = 0, show.n = T, show.all = T)
print(dt, header.labels = c(all = "Prevalencias"), which.table = "both")
export2xls(dt, file= "output/Proportions_Before and during COVID in 0 to 1 15 years.xlsx", header.labels = c(all = "Elegibles"), which.table = "both")
```


## + 0 a 4 anos
```{r}
Prev <-compareGroups(COVID ~ elegibleneumonia + 
                        elegibleili + elegibleili7 +
                        elegiblefebril_FUO + elegiblefebril7_FUO + 
                     elegiblediarrea + elegiblediarrea7,
                  data=PTam %>% filter(Period!="During COVID - All ages" & edad15=="Menor15" & edad5=="Menor5"),
                  method = c(edad=2),
                  include.label = T)

dt<-createTable(Prev, digits = 0, show.n = T, show.all = T)
print(dt, header.labels = c(all = "Prevalencias"), which.table = "both")
export2xls(dt, file= "output/Proportions_Before and during COVID in 0 to 4 years.xlsx", header.labels = c(all = "Elegibles"), which.table = "both")
```

## + 5 a 14 anos
```{r}
Prev <-compareGroups(COVID ~ elegibleneumonia + 
                        elegibleili + elegibleili7 +
                        elegiblefebril_FUO + elegiblefebril7_FUO + 
                     elegiblediarrea + elegiblediarrea7,
                  data=PTam %>% filter(Period!="During COVID - All ages" & edad15=="Menor15" & edad5=="5oMas"),
                  method = c(edad=2),
                  include.label = T)

dt<-createTable(Prev, digits = 0, show.n = T, show.all = T)
print(dt, header.labels = c(all = "Prevalencias"), which.table = "both")
export2xls(dt, file= "output/Proportions_Before and during COVID in 5 to 14 years.xlsx", header.labels = c(all = "Elegibles"), which.table = "both")
```






# 4. Prevalences


Aplicar la post estratificacion:
```{r}
PTam_S <- svydesign(id = ~cluster+id_record+IDPersona, 
                   data = PTam,
                   weights =  ~WeightCluster*WeightHouse*WeightInd)
PTam_S_Str <-postStratify(PTam_S, strata = ~Strata, population = pop3)

```


##  BEFORE COVID

```{r}
subset <- subset(PTam_S_Str, Period =="Before COVID - All ages")
```


## + Contrasts (svychisq)

Diff by age
```{r}
svychisq(~elegibleneumonia+edad5, design = subset, statistic="F")
svychisq(~elegibleili+edad5, design = subset, statistic="F")
svychisq(~elegiblefebril_FUO+edad5, design = subset, statistic="F")
svychisq(~elegiblediarrea+edad5, design = subset, statistic="F")
```

Diff by sex
```{r}
svychisq(~elegibleneumonia+sexo_des, design = subset, statistic="F")
svychisq(~elegibleili+sexo_des, design = subset, statistic="F")
svychisq(~elegiblefebril_FUO+sexo_des, design = subset, statistic="F")
svychisq(~elegiblediarrea+sexo_des, design = subset, statistic="F")
```



## + Prev: Overall (svymean)

```{r}
means <- svymean(~elegibleneumonia +
                  elegibleili + elegibleili7 +
                  elegiblefebril_FUO + elegiblefebril7_FUO + 
                  elegiblediarrea + elegiblediarrea7, 
                 subset, deff=T)

means
a<-as.data.frame(means) [c(1,3,5,7,9,11,13),]
b<-round(confint(means)[c(1,3,5,7,9,11,13),]*100)

c1<-a %>% 
  mutate(mean = round(mean*100),
         deff = round(deff,2),
         SE = round(SE,2),
         Period = "Before COVID - All ages",
         Age="All",
         Sex="All") %>%
  cbind(b) %>%
  select( Period, Age, Sex, mean, `2.5 %`, `97.5 %`, SE, deff) %>% 
  rownames_to_column()
c1
```



## + Prev: Menor5

```{r}
subset <- subset(PTam_S_Str, Period =="Before COVID - All ages" & edad5=="Menor5")
means <- svymean(~elegibleneumonia +
                  elegibleili + elegibleili7 +
                  elegiblefebril_FUO + elegiblefebril7_FUO + 
                  elegiblediarrea + elegiblediarrea7, 
                 subset, deff=T)

means
a<-as.data.frame(means) [c(1,3,5,7,9,11,13),]
b<-round(confint(means)[c(1,3,5,7,9,11,13),]*100)

c2<-a %>% 
  mutate(mean = round(mean*100),
         deff = round(deff,2),
         SE = round(SE,2),
         Period = "Before COVID - All ages",
         Age="<5",
         Sex="All") %>%
  cbind(b) %>%
  select( Period, Age, Sex, mean, `2.5 %`, `97.5 %`, SE, deff) %>%  
  rownames_to_column()

c2
```

## + Prev: 5oMas

```{r}
subset <- subset(PTam_S_Str, Period =="Before COVID - All ages" & edad5=="5oMas")
means <- svymean(~elegibleneumonia +
                  elegibleili + elegibleili7 +
                  elegiblefebril_FUO + elegiblefebril7_FUO + 
                  elegiblediarrea + elegiblediarrea7, 
                 subset, deff=T)

means
a<-as.data.frame(means) [c(1,3,5,7,9,11,13),]
b<-round(confint(means)[c(1,3,5,7,9,11,13),]*100)

c3<-a %>% 
  mutate(mean = round(mean*100),
         deff = round(deff,2),
         SE = round(SE,2),
         Period = "Before COVID - All ages",
         Age=">=5",
         Sex="All") %>%
  cbind(b) %>%
  select( Period, Age, Sex, mean, `2.5 %`, `97.5 %`, SE, deff) %>% 
  rownames_to_column()

c3
```

## + Prev: Menor5-Males

```{r}
subset <- subset(PTam_S_Str, Period =="Before COVID - All ages" & edad5=="Menor5" & sexo_des=="Masculino")
means <- svymean(~elegibleneumonia +
                  elegibleili + elegibleili7 +
                  elegiblefebril_FUO + elegiblefebril7_FUO + 
                  elegiblediarrea + elegiblediarrea7, 
                 subset, deff=T)

means
a<-as.data.frame(means) [c(1,3,5,7,9,11,13),]
b<-round(confint(means)[c(1,3,5,7,9,11,13),]*100)

c4<-a %>% 
  mutate(mean = round(mean*100),
         deff = round(deff,2),
         SE = round(SE,2),
         Period = "Before COVID - All ages",
         Age="<5",
         Sex="Males") %>%
  cbind(b) %>%
  select( Period, Age, Sex, mean, `2.5 %`, `97.5 %`, SE, deff) %>%  
  rownames_to_column()

c4
```


## + Prev: Menor5-Females

```{r}
subset <- subset(PTam_S_Str, Period =="Before COVID - All ages" & edad5=="Menor5" & sexo_des=="Femenino")
means <- svymean(~elegibleneumonia +
                  elegibleili + elegibleili7 +
                  elegiblefebril_FUO + elegiblefebril7_FUO + 
                  elegiblediarrea + elegiblediarrea7, 
                 subset, deff=T)

means
a<-as.data.frame(means) [c(1,3,5,7,9,11,13),]
b<-round(confint(means)[c(1,3,5,7,9,11,13),]*100)

c5<-a %>% 
  mutate(mean = round(mean*100),
         deff = round(deff,2),
         SE = round(SE,2),
         Period = "Before COVID - All ages",
         Age="<5",
         Sex="Females") %>%
  cbind(b) %>%
  select( Period, Age, Sex, mean, `2.5 %`, `97.5 %`, SE, deff) %>%  
  rownames_to_column()

c5
```

## + Prev: 5oMas-Males

```{r}
subset <- subset(PTam_S_Str, Period =="Before COVID - All ages" & edad5=="5oMas" & sexo_des=="Masculino")
means <- svymean(~elegibleneumonia +
                  elegibleili + elegibleili7 +
                  elegiblefebril_FUO + elegiblefebril7_FUO + 
                  elegiblediarrea + elegiblediarrea7, 
                 subset, deff=T)

means
a<-as.data.frame(means) [c(1,3,5,7,9,11,13),]
b<-round(confint(means)[c(1,3,5,7,9,11,13),]*100)

c6<-a %>% 
  mutate(mean = round(mean*100),
         deff = round(deff,2),
         SE = round(SE,2),
         Period = "Before COVID - All ages",
         Age=">=5",
         Sex="Males") %>%
  cbind(b) %>%
  select( Period, Age, Sex, mean, `2.5 %`, `97.5 %`, SE, deff) %>%  
  rownames_to_column()

c6
```


## + Prev: 5oMas-Females

```{r}
subset <- subset(PTam_S_Str, Period =="Before COVID - All ages" & edad5=="5oMas" & sexo_des=="Femenino")
means <- svymean(~elegibleneumonia +
                  elegibleili + elegibleili7 +
                  elegiblefebril_FUO + elegiblefebril7_FUO + 
                  elegiblediarrea + elegiblediarrea7, 
                 subset, deff=T)

means
a<-as.data.frame(means) [c(1,3,5,7,9,11,13),]
b<-round(confint(means)[c(1,3,5,7,9,11,13),]*100)

c7<-a %>% 
  mutate(mean = round(mean*100),
         deff = round(deff,2),
         SE = round(SE,2),
         Period = "Before COVID - All ages",
         Age=">=5",
         Sex="Females") %>%
  cbind(b) %>%
  select( Period, Age, Sex, mean, `2.5 %`, `97.5 %`, SE, deff) %>%  
  rownames_to_column()

c7
```



## + Bind

```{r}
C <- bind_rows(c1, c2, c3, c4, c5, c6, c7)
C

write_rds(C, "output/Prevalences_PreCOVID_AllAges.rds")
writexl::write_xlsx(C, "output/Prevalences_PreCOVID_AllAges.xlsx")
```





## BEFORE AND DURING COVID


## + Prev: Before - 0to14 (svymean)

```{r}
subset <- subset(PTam_S_Str, Period=="Before COVID - All ages" & edad15=="Menor15")

means <- svymean(~elegibleneumonia +
                  elegibleili + elegibleili7 +
                  elegiblefebril_FUO + elegiblefebril7_FUO + 
                  elegiblediarrea + elegiblediarrea7, 
                 subset, deff=T)

a<-as.data.frame(means) [c(1,3,5,7,9,11,13),]
b<-round(confint(means)[c(1,3,5,7,9,11,13),]*100)

c1<-a %>% 
  mutate(mean = round(mean*100),
         deff = round(deff,2),
         SE = round(SE,2),
         Period = "Before COVID - All ages",
         Age="0to14",
         Sex="All") %>%
  cbind(b) %>%
  select( Period, Age, Sex, mean, `2.5 %`, `97.5 %`, SE, deff) %>% 
  rownames_to_column()
c1
```


## + Prev: Before - 0to4

```{r}
PTam %>% filter(Period=="Before COVID - All ages" & edad5=="Menor5") %>% count(Period, edad15, edad5)
subset <- subset(PTam_S_Str, Period=="Before COVID - All ages" & edad5=="Menor5")

means <- svymean(~elegibleneumonia +
                  elegibleili + elegibleili7 +
                  elegiblefebril_FUO + elegiblefebril7_FUO + 
                  elegiblediarrea + elegiblediarrea7, 
                 subset, deff=T)
a<-as.data.frame(means) [c(1,3,5,7,9,11,13),]
b<-round(confint(means)[c(1,3,5,7,9,11,13),]*100)

c2<-a %>% 
  mutate(mean = round(mean*100),
         deff = round(deff,2),
         SE = round(SE,2),
         Period = "Before COVID - All ages",
         Age="0to4",
         Sex="All") %>%
  cbind(b) %>%
  select( Period, Age, Sex, mean, `2.5 %`, `97.5 %`, SE, deff) %>% 
  rownames_to_column()
c2
```


## + Prev: Before - 5to14

```{r}
PTam %>% filter(Period=="Before COVID - All ages" & edad5=="5oMas" & edad15=="Menor15") %>% count(Period, edad15, edad5)


subset <- subset(PTam_S_Str, Period=="Before COVID - All ages" & edad5=="5oMas" & edad15=="Menor15")

means <- svymean(~elegibleneumonia +
                  elegibleili + elegibleili7 +
                  elegiblefebril_FUO + elegiblefebril7_FUO + 
                  elegiblediarrea + elegiblediarrea7, 
                 subset, deff=T)

a<-as.data.frame(means) [c(1,3,5,7,9,11,13),]
b<-round(confint(means)[c(1,3,5,7,9,11,13),]*100)

c3<-a %>% 
  mutate(mean = round(mean*100),
         deff = round(deff,2),
         SE = round(SE,2),
         Period = "Before COVID - All ages",
         Age="5to14",
         Sex="All") %>%
  cbind(b) %>%
  select( Period, Age, Sex, mean, `2.5 %`, `97.5 %`, SE, deff) %>% 
  rownames_to_column()
c3
```


## + Prev: During - 0to14

```{r}
PTam %>% filter(Period=="During COVID - <15 years" & edad15=="Menor15") %>% count(Period, edad15, edad5)
subset <- subset(PTam_S_Str, Period=="During COVID - <15 years" & edad15=="Menor15")

means <- svymean(~elegibleneumonia +
                  elegibleili + elegibleili7 +
                  elegiblefebril_FUO + elegiblefebril7_FUO + 
                  elegiblediarrea + elegiblediarrea7, 
                 subset, deff=T)

a<-as.data.frame(means) [c(1,3,5,7,9,11,13),]
b<-round(confint(means)[c(1,3,5,7,9,11,13),]*100)

c4<-a %>% 
  mutate(mean = round(mean*100),
         deff = round(deff,2),
         SE = round(SE,2),
         Period = "During COVID - <15 years",
         Age="0to14",
         Sex="All") %>%
  cbind(b) %>%
  select( Period, Age, Sex, mean, `2.5 %`, `97.5 %`, SE, deff) %>% 
  rownames_to_column()
c4
```


## + Prev: During - 0to4

```{r}
PTam %>% filter(Period=="During COVID - <15 years" & edad5=="Menor5") %>% count(Period, edad15, edad5)
subset <- subset(PTam_S_Str, Period=="During COVID - <15 years" & edad5=="Menor5")

means <- svymean(~elegibleneumonia +
                  elegibleili + elegibleili7 +
                  elegiblefebril_FUO + elegiblefebril7_FUO + 
                  elegiblediarrea + elegiblediarrea7, 
                 subset, deff=T)
a<-as.data.frame(means) [c(1,3,5,7,9,11,13),]
b<-round(confint(means)[c(1,3,5,7,9,11,13),]*100)

c5<-a %>% 
  mutate(mean = round(mean*100),
         deff = round(deff,2),
         SE = round(SE,2),
         Period = "During COVID - <15 years",
         Age="0to4",
         Sex="All") %>%
  cbind(b) %>%
  select( Period, Age, Sex, mean, `2.5 %`, `97.5 %`, SE, deff) %>% 
  rownames_to_column()
c5
```


## + Prev: During - 5to14

```{r}
PTam %>% filter(Period=="During COVID - <15 years" & edad5=="5oMas" & edad15=="Menor15") %>% count(Period, edad15, edad5)


subset <- subset(PTam_S_Str, Period=="During COVID - <15 years" & edad5=="5oMas" & edad15=="Menor15")

means <- svymean(~elegibleneumonia +
                  elegibleili + elegibleili7 +
                  elegiblefebril_FUO + elegiblefebril7_FUO + 
                  elegiblediarrea + elegiblediarrea7, 
                 subset, deff=T)

a<-as.data.frame(means) [c(1,3,5,7,9,11,13),]
b<-round(confint(means)[c(1,3,5,7,9,11,13),]*100)

c6<-a %>% 
  mutate(mean = round(mean*100),
         deff = round(deff,2),
         SE = round(SE,2),
         Period = "During COVID - <15 years",
         Age="5to14",
         Sex="All") %>%
  cbind(b) %>%
  select( Period, Age, Sex, mean, `2.5 %`, `97.5 %`, SE, deff) %>% 
  rownames_to_column()
c6
```

## + Bind

```{r}
C <- bind_rows(c1, c2, c3, c4, c5, c6)
C

write_rds(C, "output/Prevalences_BeforeAfterCovid_Children.rds")
writexl::write_xlsx(C, "output/Prevalences_BeforeAfterCovid_Children.xlsx")
```


## + Contrasts (svychist)

Diff by covid among 0 to 14
```{r}
subset <- subset(PTam_S_Str, Period!="During COVID - All ages" & edad15=="Menor15")
svychisq(~elegibleneumonia+COVID, design = subset, statistic="F")
svychisq(~elegibleili+COVID, design = subset, statistic="F")
svychisq(~elegibleili7+COVID, design = subset, statistic="F")
svychisq(~elegiblefebril_FUO+COVID, design = subset, statistic="F")
svychisq(~elegiblefebril7_FUO+COVID, design = subset, statistic="F")
svychisq(~elegiblediarrea+COVID, design = subset, statistic="F")
svychisq(~elegiblediarrea7+COVID, design = subset, statistic="F")
```

Diff by covid among 0 to 4
```{r}
subset <- subset(PTam_S_Str, Period!="During COVID - All ages" & edad15=="Menor15" & edad5=="Menor5")
svychisq(~elegibleneumonia+COVID, design = subset, statistic="F")
svychisq(~elegibleili+COVID, design = subset, statistic="F")
svychisq(~elegibleili7+COVID, design = subset, statistic="F")
svychisq(~elegiblefebril_FUO+COVID, design = subset, statistic="F")
svychisq(~elegiblefebril7_FUO+COVID, design = subset, statistic="F")
svychisq(~elegiblediarrea+COVID, design = subset, statistic="F")
svychisq(~elegiblediarrea7+COVID, design = subset, statistic="F")
```
Diff by covid among 4 to 14
```{r}
subset <- subset(PTam_S_Str, Period!="During COVID - All ages" & edad15=="Menor15" & edad5=="5oMas")
svychisq(~elegibleneumonia+COVID, design = subset, statistic="F")
svychisq(~elegibleili+COVID, design = subset, statistic="F")
svychisq(~elegibleili7+COVID, design = subset, statistic="F")
svychisq(~elegiblefebril_FUO+COVID, design = subset, statistic="F")
svychisq(~elegiblefebril7_FUO+COVID, design = subset, statistic="F")
svychisq(~elegiblediarrea+COVID, design = subset, statistic="F")
svychisq(~elegiblediarrea7+COVID, design = subset, statistic="F")
```



# 5. Odds ratios

## COMPARE BEFORE AND DURING COVID




## + Overall

Penumonia
```{r}
PTam %>% filter(Period!="During COVID - All ages" & edad15=="Menor15") %>% count(Period, edad15, edad5)

subset <- subset(PTam_S_Str, Period!="During COVID - All ages" & edad15=="Menor15")


# Prevalence ratios
M<-svyglm(elegibleneumonia_num ~ COVID + 
          idiomahogar_des + hacinamiento_cat + 
          combustiblecocinaprincipal_cal + fuenteagua_cal + sanitario_cal + 
          SES_Tertiles +
          sexo_des + edadcat, 
          design = subset, family = quasipoisson(link = "log"))

SPR_1 <- tidy(M, exponentiate = TRUE, conf.int = TRUE) |> 
  filter(term=="COVIDDuring") %>% 
  mutate(across(c(estimate, std.error, statistic, conf.low, conf.high), ~ round(.x, 2))) |> 
  mutate(Age = "<15",
         Sx = "Pneumonia")
SPR_1


# odds ratios
M<-svyglm(elegibleneumonia_num ~ COVID + 
          idiomahogar_des + hacinamiento_cat + 
          combustiblecocinaprincipal_cal + fuenteagua_cal + sanitario_cal + 
          SES_Tertiles +
          sexo_des + edadcat, 
          design = subset, family = quasibinomial(link = "logit"))

tidy(M, exponentiate = TRUE, conf.int = TRUE) |> 
  filter(term=="COVIDDuring") %>% 
  mutate(across(c(estimate, std.error, statistic, conf.low, conf.high), ~ round(.x, 2)))
```

```{r}
PTam %>% filter(Period!="During COVID - All ages" & edad15=="Menor15" ) 

sub <- subset(PTam_S_Str, Period!="During COVID - All ages" & edad15=="Menor15")


# Prevalence ratios
M<-svyglm(elegibleili_num ~ COVID + 
          idiomahogar_des + hacinamiento_cat + 
          combustiblecocinaprincipal_cal + fuenteagua_cal + sanitario_cal + 
          SES_Tertiles +
          sexo_des + edadcat, 
          design = sub, family = quasipoisson(link = "log"))

SPR_2 <- tidy(M, exponentiate = TRUE, conf.int = TRUE) |> 
  filter(term=="COVIDDuring") %>% 
  mutate(across(c(estimate, std.error, statistic, conf.low, conf.high), ~ round(.x, 2))) |> 
  mutate(Age = "<15",
         Sx = "ILI")
SPR_2



# odds ratios
M<-svyglm(elegibleili_num ~ COVID + 
          idiomahogar_des + hacinamiento_cat + 
          combustiblecocinaprincipal_cal + fuenteagua_cal + sanitario_cal + 
          SES_Tertiles +
          sexo_des + edadcat, 
          design = subset, family = quasibinomial(link = "logit"))

tidy(M, exponentiate = TRUE, conf.int = TRUE) |> 
  filter(term=="COVIDDuring") %>% 
  mutate(across(c(estimate, std.error, statistic, conf.low, conf.high), ~ round(.x, 2)))
```

```{r}
PTam %>% filter(Period!="During COVID - All ages" & edad15=="Menor15") %>% count(Period, edad15, edad5)

subset <- subset(PTam_S_Str, Period!="During COVID - All ages" & edad15=="Menor15")

# Prevalence ratio
M<-svyglm(elegiblefebril_FUO_num ~ COVID + 
          idiomahogar_des + hacinamiento_cat + 
          combustiblecocinaprincipal_cal + fuenteagua_cal + sanitario_cal + 
          SES_Tertiles +
          sexo_des + edadcat, 
          design = subset, family = quasipoisson(link = "log"))

SPR_3 <- tidy(M, exponentiate = TRUE, conf.int = TRUE) |> 
  filter(term=="COVIDDuring") %>% 
  mutate(across(c(estimate, std.error, statistic, conf.low, conf.high), ~ round(.x, 2))) |> 
  mutate(Age = "<15",
         Sx = "FUO")
SPR_3


# odds ratios
M<-svyglm(elegiblefebril_FUO_num ~ COVID + 
          idiomahogar_des + hacinamiento_cat + 
          combustiblecocinaprincipal_cal + fuenteagua_cal + sanitario_cal + 
          SES_Tertiles +
          sexo_des + edadcat, 
          design = subset, family = quasibinomial(link = "logit"))

tidy(M, exponentiate = TRUE, conf.int = TRUE) |> 
  filter(term=="COVIDDuring") %>% 
  mutate(across(c(estimate, std.error, statistic, conf.low, conf.high), ~ round(.x, 2)))
```

```{r}
PTam %>% filter(Period!="During COVID - All ages" & edad15=="Menor15") %>% count(Period, edad15, edad5)

subset <- subset(PTam_S_Str, Period!="During COVID - All ages" & edad15=="Menor15")

# Prevalence ratio
M<-svyglm(elegiblediarrea_num ~ COVID + 
          idiomahogar_des + hacinamiento_cat + 
          combustiblecocinaprincipal_cal + fuenteagua_cal + sanitario_cal + 
          SES_Tertiles +
          sexo_des + edadcat, 
          design = subset, family = quasipoisson(link = "log"))

SPR_4 <- tidy(M, exponentiate = TRUE, conf.int = TRUE) |> 
  filter(term=="COVIDDuring") %>% 
  mutate(across(c(estimate, std.error, statistic, conf.low, conf.high), ~ round(.x, 2))) |> 
  mutate(Age = "<15",
         Sx = "Diarrea")
SPR_4


# odds ratios
M<-svyglm(elegiblediarrea_num ~ COVID + 
          idiomahogar_des + hacinamiento_cat + 
          combustiblecocinaprincipal_cal + fuenteagua_cal + sanitario_cal + 
          SES_Tertiles +
          sexo_des + edadcat, 
          design = subset, family = quasibinomial(link = "logit"))

tidy(M, exponentiate = TRUE, conf.int = TRUE) |> 
  filter(term=="COVIDDuring") %>% 
  mutate(across(c(estimate, std.error, statistic, conf.low, conf.high), ~ round(.x, 2)))
```



## + 0-4

```{r}
PTam %>% filter(Period!="During COVID - All ages" & edad5=="Menor5") %>% count(Period, edad15, edad5)

subset <- subset(PTam_S_Str, Period!="During COVID - All ages" & edad5=="Menor5")
M<-svyglm(elegibleneumonia_num ~ COVID + 
          idiomahogar_des + hacinamiento_cat + 
          combustiblecocinaprincipal_cal + fuenteagua_cal + sanitario_cal + 
          SES_Tertiles +
          sexo_des + edadcat, 
          design = subset, family = quasipoisson(link = "log"))

SPR_5 <- tidy(M, exponentiate = TRUE, conf.int = TRUE) |> 
  filter(term=="COVIDDuring") %>% 
  mutate(across(c(estimate, std.error, statistic, conf.low, conf.high), ~ round(.x, 2))) |> 
  mutate(Age = "0-4",
         Sx = "Neumonia")
SPR_5
```

```{r}
PTam %>% filter(Period!="During COVID - All ages" & edad5=="Menor5") %>% count(Period, edad15, edad5)

subset <- subset(PTam_S_Str, Period!="During COVID - All ages" & edad5=="Menor5")
M<-svyglm(elegibleili_num ~ COVID + 
          idiomahogar_des + hacinamiento_cat + 
          combustiblecocinaprincipal_cal + fuenteagua_cal + sanitario_cal + 
          SES_Tertiles +
          sexo_des + edadcat, 
          design = subset, family = quasipoisson(link = "log"))

SPR_6 <- tidy(M, exponentiate = TRUE, conf.int = TRUE) |> 
  filter(term=="COVIDDuring") %>% 
  mutate(across(c(estimate, std.error, statistic, conf.low, conf.high), ~ round(.x, 2))) |> 
  mutate(Age = "0-4",
         Sx = "ILI")
SPR_6
```

```{r}
PTam %>% filter(Period!="During COVID - All ages" & edad5=="Menor5") %>% count(Period, edad15, edad5, elegiblefebril_FUO)

subset <- subset(PTam_S_Str, Period!="During COVID - All ages" & edad5=="Menor5")
M<-svyglm(elegiblefebril_FUO_num ~ COVID + 
          idiomahogar_des + hacinamiento_cat + 
          combustiblecocinaprincipal_cal + fuenteagua_cal + sanitario_cal + 
          SES_Tertiles +
          sexo_des + edadcat, 
          design = subset, family = quasipoisson(link = "log"))

SPR_7 <- tidy(M, exponentiate = TRUE, conf.int = TRUE) |> 
  filter(term=="COVIDDuring") %>% 
  mutate(across(c(estimate, std.error, statistic, conf.low, conf.high), ~ round(.x, 2))) |> 
  mutate(Age = "0-4",
         Sx = "FUO")
SPR_7
```

```{r}
PTam %>% filter(Period!="During COVID - All ages" & edad5=="Menor5") %>% count(Period, edad15, edad5, elegiblefebril_FUO)

subset <- subset(PTam_S_Str, Period!="During COVID - All ages" & edad5=="Menor5")
M<-svyglm(elegiblediarrea_num ~ COVID + 
          idiomahogar_des + hacinamiento_cat + 
          combustiblecocinaprincipal_cal + fuenteagua_cal + sanitario_cal + 
          SES_Tertiles +
          sexo_des + edadcat, 
          design = subset, family = quasipoisson(link = "log"))

SPR_8 <- tidy(M, exponentiate = TRUE, conf.int = TRUE) |> 
  filter(term=="COVIDDuring") %>% 
  mutate(across(c(estimate, std.error, statistic, conf.low, conf.high), ~ round(.x, 2))) |> 
  mutate(Age = "0-4",
         Sx = "Diarrea")
SPR_8
```

## + 5-14

```{r}
PTam %>% filter(Period!="During COVID - All ages" & edad15=="Menor15" & edad5=="5oMas") %>% count(Period, edad15, edad5)

subset <- subset(PTam_S_Str, Period!="During COVID - All ages" & edad15=="Menor15" & edad5=="5oMas")
M<-svyglm(elegibleneumonia_num ~ COVID + 
          idiomahogar_des + hacinamiento_cat + 
          combustiblecocinaprincipal_cal + fuenteagua_cal + sanitario_cal + 
          SES_Tertiles +
          sexo_des + edadcat, 
          design = subset, family = quasipoisson(link = "log"))

SPR_9 <- tidy(M, exponentiate = TRUE, conf.int = TRUE) |> 
  filter(term=="COVIDDuring") %>% 
  mutate(across(c(estimate, std.error, statistic, conf.low, conf.high), ~ round(.x, 2))) |> 
  mutate(Age = "5-14",
         Sx = "Neumonia")
SPR_9
```

```{r}
PTam %>% filter(Period!="During COVID - All ages" & edad15=="Menor15" & edad5=="5oMas") %>% count(Period, edad15, edad5)

subset <- subset(PTam_S_Str, Period!="During COVID - All ages" & edad15=="Menor15" & edad5=="5oMas")
M<-svyglm(elegibleili_num ~ COVID + 
         idiomahogar_des + hacinamiento_cat + 
          combustiblecocinaprincipal_cal + fuenteagua_cal + sanitario_cal + 
          SES_Tertiles +
          sexo_des + edadcat, 
          design = subset, family = quasipoisson(link = "log"))

SPR_10 <- tidy(M, exponentiate = TRUE, conf.int = TRUE) |> 
  filter(term=="COVIDDuring") %>% 
  mutate(across(c(estimate, std.error, statistic, conf.low, conf.high), ~ round(.x, 2))) |> 
  mutate(Age = "5-14",
         Sx = "ILI")
SPR_10
```

```{r}
PTam %>% filter(Period!="During COVID - All ages" & edad15=="Menor15" & edad5=="5oMas") %>% count(Period, edad15, edad5, elegiblefebril_FUO)

subset <- subset(PTam_S_Str, Period!="During COVID - All ages" & edad15=="Menor15" & edad5=="5oMas")


M<-svyglm(elegiblefebril_FUO_num ~ COVID + 
          idiomahogar_des + hacinamiento_cat + 
          combustiblecocinaprincipal_cal + fuenteagua_cal + sanitario_cal + 
          SES_Tertiles +
          sexo_des + edadcat, 
          design = subset, family = quasipoisson(link = "log"))

SPR_11 <- tidy(M, exponentiate = TRUE, conf.int = TRUE) |> 
  filter(term=="COVIDDuring") %>% 
  mutate(across(c(estimate, std.error, statistic, conf.low, conf.high), ~ round(.x, 2))) |> 
  mutate(Age = "5-14",
         Sx = "FUO")
SPR_11
```



```{r}
PTam %>% filter(Period!="During COVID - All ages" & edad15=="Menor15" & edad5=="5oMas") %>% count(Period, edad15, edad5, elegiblefebril_FUO)

subset <- subset(PTam_S_Str, Period!="During COVID - All ages" & edad15=="Menor15" & edad5=="5oMas")
M<-svyglm(elegiblediarrea_num ~ COVID + 
          idiomahogar_des + hacinamiento_cat + 
          combustiblecocinaprincipal_cal + fuenteagua_cal + sanitario_cal + 
          SES_Tertiles +
          sexo_des + edadcat, 
          design = subset, family = quasipoisson(link = "log"))

SPR_12 <- tidy(M, exponentiate = TRUE, conf.int = TRUE) |> 
  filter(term=="COVIDDuring") %>% 
  mutate(across(c(estimate, std.error, statistic, conf.low, conf.high), ~ round(.x, 2))) |> 
  mutate(Age = "5-14",
         Sx = "Diarrea")
SPR_12
```


## + Bind


```{r}
C <- bind_rows(SPR_1, SPR_2, SPR_3, SPR_4,
               SPR_5, SPR_6, SPR_7, SPR_8,
               SPR_9, SPR_10, SPR_11, SPR_12)
C

write_rds(C, "output/PrevalenceRatios_BeforeAfterCovid_Children.rds")
writexl::write_xlsx(C, "output/PrevalenceRatios_BeforeAfterCovid_Children.xlsx")
```

```{r}
class(PTam$elegiblediarrea_num)
class(PTam$COVID)
class(PTam$idiomahogar_des)
class(PTam$hacinamiento_cat)
class(PTam$combustiblecocinaprincipal_cal)
class(PTam$fuenteagua_cal)
class(PTam$sanitario_cal)
class(PTam$SES_Tertiles)
class(PTam$sexo_des)
class(PTam$edadcat)
```




## THE END