---
title: "Untitled"
output: html_document
date: "2022-10-11"
---

```{r}
library(tidyverse)
library(survey)
library(reshape)
```
Meeting on Tuesday- identify excel 360 and identify up to what cluster we include


Clarify with Doug---
3-stage sampling:
Clusters
Casas
Individuos 

We have 6 weights, 2 for each sampling unit

# 1. Objetivo

Calcular los pesos de la primera fase de la encuesta, hasta el tamizaje. Estos me serviran para obtener las prevalencias por sindrome. The same procedure will be followed for ESCrE and CRE
  

# 2. Datos


```{r warning=FALSE, echo=F, message=FALSE, results='hide'}
  if (!require("RMySQL"))    {install.packages("RMySQL");   library("RMySQL")}
  conRedcap <- dbConnect(MySQL(), user="redcapdb", password="4S3rr3dc4p.2017++",
                          dbname="redcap", host="144.217.19.237")
  
  clustersVis <- dbGetQuery(conRedcap, "select * from identificacion_cluster_amr_vicoip")
  hogares <- dbGetQuery(conRedcap, "select * from identificacion_de_hogares_amr_vicoip")
  hogaresVis <- dbGetQuery(conRedcap, "SELECT * FROM amr_datos_hogar")
  P1 <- dbGetQuery(conRedcap, "SELECT * FROM amr_tamizaje_p1")
  P2 <- dbGetQuery(conRedcap, "SELECT * FROM amr_tamizaje_p2")
  P3 <- dbGetQuery(conRedcap, "SELECT * FROM amr_tamizaje_p3")
  P4 <- dbGetQuery(conRedcap, "SELECT * FROM amr_tamizaje_p4")
  P5 <- dbGetQuery(conRedcap, "SELECT * FROM amr_tamizaje_p5")
  P6 <- dbGetQuery(conRedcap, "SELECT * FROM amr_tamizaje_p6")
  P7 <- dbGetQuery(conRedcap, "SELECT * FROM amr_tamizaje_p7")
  P8 <- dbGetQuery(conRedcap, "SELECT * FROM amr_tamizaje_p8")
  P9 <- dbGetQuery(conRedcap, "SELECT * FROM amr_tamizaje_p9")
  P10 <- dbGetQuery(conRedcap, "SELECT * FROM amr_tamizaje_p10")
  P11 <- dbGetQuery(conRedcap, "SELECT * FROM amr_tamizaje_p11")
  P12 <- dbGetQuery(conRedcap, "SELECT * FROM amr_tamizaje_12")
  P13 <- dbGetQuery(conRedcap, "SELECT * FROM amr_tamizaje_p13")
  P14 <- dbGetQuery(conRedcap, "SELECT * FROM amr_tamizaje_p14")
  P15 <- dbGetQuery(conRedcap, "SELECT * FROM amr_tamizaje_p15")
  ind <- dbGetQuery(conRedcap, "SELECT * FROM amr_informe_caso")
 dbDisconnect(conRedcap)
```


Quitar los registros que no son hogres de la tabla de conteo de viviendas
```{r}
 hogares <- hogares %>%
   filter(record_id!="A010-007") %>% # hogar esta afuera del cluster
   filter(record_id!="A073-001") %>% # se confirmo que la vivienda esta deshabitada
   filter(record_id!="A073-003") %>% # se confirmo que la vivienda esta deshabitada
   filter(record_id!="A131-009") %>% # Familia pertenece al hogar A131-008
   filter(record_id!="A131-013") %>% # Familia pertenece al hogar A131-012
   filter(record_id!="A075-004") %>% # se confirmo que la vivienda esta deshabitada
   filter(record_id!="A067-017") %>% # se confirmo que la vivienda esta deshabitada
   filter(record_id!="A129-001") # Familia pertenece al hogar A129-002
```

#Cantidad Personas, ninos, adultos ESTUDIO
#the following code is to verify that the calculation used to verify the kdis is being done correctly
```{r}
hogaresVis$edadp1 <- as.numeric(hogaresVis$edadp1)
hogaresVis$edadp2 <- as.numeric(hogaresVis$edadp2)
hogaresVis$edadp3 <- as.numeric(hogaresVis$edadp3)
hogaresVis$edadp4 <- as.numeric(hogaresVis$edadp4)
hogaresVis$edadp5 <- as.numeric(hogaresVis$edadp5)
hogaresVis$edadp6 <- as.numeric(hogaresVis$edadp6)
hogaresVis$edadp7 <- as.numeric(hogaresVis$edadp7)
hogaresVis$edadp8 <- as.numeric(hogaresVis$edadp8)
hogaresVis$edadp9 <- as.numeric(hogaresVis$edadp9)
hogaresVis$edadp10 <- as.numeric(hogaresVis$edadp10)
hogaresVis$edadp11 <- as.numeric(hogaresVis$edadp11)
hogaresVis$edadp12 <- as.numeric(hogaresVis$edadp12)
hogaresVis$edadp13 <- as.numeric(hogaresVis$edadp13)
hogaresVis$edadp14 <- as.numeric(hogaresVis$edadp14)
hogaresVis$edadp15 <- as.numeric(hogaresVis$edadp15)
hogaresVis <- hogaresVis %>% 
  mutate(
        HayP1 = ifelse(!is.na(nombrep1),1,0),
         HayP2 = ifelse(!is.na(nombrep2),1,0),
         HayP3 = ifelse(!is.na(nombrep3),1,0),
         HayP4 = ifelse(!is.na(nombrep4),1,0),
         HayP5 = ifelse(!is.na(nombrep5),1,0),
         HayP6 = ifelse(!is.na(nombrep6),1,0),
         HayP7 = ifelse(!is.na(nombrep7),1,0),
         HayP8 = ifelse(!is.na(nombrep8),1,0),
         HayP9 = ifelse(!is.na(nombrep9),1,0),
         HayP10 = ifelse(!is.na(nombrep10),1,0),
         HayP11 = ifelse(!is.na(nombrep11),1,0),
         HayP12 = ifelse(!is.na(nombrep12),1,0),
         HayP13 = ifelse(!is.na(nombrep13),1,0),
         HayP14 = ifelse(!is.na(nombrep14),1,0),
         HayP15 = ifelse(!is.na(nombrep15),1,0)
  ) %>% mutate(
    TotalP = rowSums(.[grep("HayP", names(.))])
  ) %>% mutate(
         HayN1 = ifelse(!is.na(nombrep1)& edadp1<15,1,0),
         HayN2 = ifelse(!is.na(nombrep2)& edadp2<15,1,0),
         HayN3 = ifelse(!is.na(nombrep3)& edadp3<15,1,0),
         HayN4 = ifelse(!is.na(nombrep4)& edadp4<15,1,0),
         HayN5 = ifelse(!is.na(nombrep5)& edadp5<15,1,0),
         HayN6 = ifelse(!is.na(nombrep6)& edadp6<15,1,0),
         HayN7 = ifelse(!is.na(nombrep7)& edadp7<15,1,0),
         HayN8 = ifelse(!is.na(nombrep8)& edadp8<15,1,0),
         HayN9 = ifelse(!is.na(nombrep9)& edadp9<15,1,0),
         HayN10 = ifelse(!is.na(nombrep10)& edadp10<15,1,0),
         HayN11 = ifelse(!is.na(nombrep11)& edadp11<15,1,0),
         HayN12 = ifelse(!is.na(nombrep12)& edadp12<15,1,0),
         HayN13 = ifelse(!is.na(nombrep13)& edadp13<15,1,0),
         HayN14 = ifelse(!is.na(nombrep14)& edadp14<15,1,0),
         HayN15 = ifelse(!is.na(nombrep15)& edadp15<15,1,0)
   ) %>% mutate(
     TotalN = rowSums(.[grep("HayN", names(.))])
   ) %>% mutate(
     cluster = str_sub(id_record, 1, 4),
     NumCluster = as.numeric( str_sub(id_record, 2, 4)),
     TipoCluster = ifelse(NumCluster >= 230 , "WT", "AMR")
   ) 

hogaresVisWT <- hogaresVis %>% filter(TipoCluster == "WT")
hogaresVisAMR <- hogaresVis %>% filter(TipoCluster == "AMR")



```

# Hogares con ninos Censados con don Nazario
# the following chunk is used to produce the data set that will be used to produce "mk"
```{r}



hogares <- hogares %>% mutate(
  HayN = if_else(
    anhos_15 > 0 | anhos_15 == "" | anhos_5 > 0 , 1, 0
  )
) %>%   mutate(
     cluster = str_sub(id_record, 1, 4),
     NumCluster = as.numeric( str_sub(id_record, 2, 4)),
     TipoCluster = ifelse(NumCluster >= 230 , "WT", "AMR")
   ) 

hogaresWT <- hogares %>% filter(TipoCluster == "WT")
hogaresAMR <- hogares %>% filter(TipoCluster == "AMR")

#the number of households that were on the selection list for Carmen
#use this filtered data set to calculate # mik is the number of households selected in PSUi and stratum k (all of the houses that were selected) instead of hogaresVis
#this will produce "mk"

hogaresWT_n <- hogares %>% filter(TipoCluster == "WT") %>% filter(HayN == 1)



```



#clusters- this is the most updated version of the cluster list. The excel file is copied here and in the prevalence manuscript folde
#Para AMR se usaron de A001-A230
#Para WT se usaron de A231 - A496
```{r}


library(readxl)
# setwd("C:/Users/bramay/Dropbox/AMR CoAg Fy18/Wellcome Trust/calculo PTam")
# clusters<- read_excel("Datos_Sel_AMR_HUS_NameClsuster.xlsx")

# Archivo que me paso Brooke
clusters<-read_excel(here("1. Calculo de pesos en individuos tamizados/input/Datos_Sel_AMR_HUS_NameClsuster.xlsx"))

```


# 3. Crear tabla de datos de las personas tamizadas

Individuos tamizados
```{r}

#This is the person that was selected, select the ones that have values to take out blank values, there were up to 15 spaces and most housesholds did not have 15 people  

#The other variables will help to have the weights for eligible participants 

P1Sel <- P1 %>% 
  dplyr::filter(!is.na(codigoentrevista_p)) %>% 
  select(id_record, "municipio"=municipio_p, "municipio_des"=municipio_p_des,
         "cluster"=cluster_p, "codigovivienda"=codigovivienda_p,
         "fechaintento1"=fechaintento1_p, "participacioninvita"=participacioninvita_p,
         "elegiblefebril"=elegiblefebril_p, "elegiblefebril7"=elegiblefebril7dias_p,
         "elegiblediarrea"=elegiblediarrea_p, "elegiblediarrea7"=elegiblediarrea7dias_p,
         "elegibleili"=elegibleili_p, "elegibleili7"=elegibleili7dias_p,
         "elegibleneumonia"=elegibleneumonia_p, "elegibleneumonia7"=elegibleneumonia7dias_p,
         "enfermedadaun"=enfermedadaun_p,
         "consentimientorecibio"=consentimientorecibio_p,
         "asentimientorecibio"=asentimientorecibio_p) %>%
   mutate(IDPersona= paste0(id_record,"-01")) #add a dash-one to keep track of the order of people in the household

P2Sel <- P2 %>% 
  dplyr::filter(!is.na(codigoentrevista_p2))%>%
   select(id_record, "municipio"=municipio_p2, "municipio_des"=municipio_p2_des,
         "cluster"=cluster_p2, "codigovivienda"=codigovivienda_p2,
         "fechaintento1"=fechaintento1_p2, "participacioninvita"=participacioninvita_p2,
         "elegiblefebril"=elegiblefebril_p2, "elegiblefebril7"=elegiblefebril7dias_p2,
         "elegiblediarrea"=elegiblediarrea_p2, "elegiblediarrea7"=elegiblediarrea7dias_p2,
         "elegibleili"=elegibleili_p2, "elegibleili7"=elegibleili7dias_p2,
         "elegibleneumonia"=elegibleneumonia_p2, "elegibleneumonia7"=elegibleneumonia7dias_p2,
         "enfermedadaun"=enfermedadaun_p2,
         "consentimientorecibio"=consentimientorecibio_p2,
         "asentimientorecibio"=asentimientorecibio_p2) %>%
   mutate(IDPersona= paste0(id_record,"-02"))


P3Sel <- P3 %>% 
  dplyr::filter(!is.na(codigoentrevista_p3))%>%
  select(id_record, "municipio"=municipio_p3, "municipio_des"=municipio_p3_des,
         "cluster"=cluster_p3, "codigovivienda"=codigovivienda_p3,
         "fechaintento1"=fechaintento1_p3, "participacioninvita"=participacioninvita_p3,
         "elegiblefebril"=elegiblefebril_p3, "elegiblefebril7"=elegiblefebril7dias_p3,
         "elegiblediarrea"=elegiblediarrea_p3, "elegiblediarrea7"=elegiblediarrea7dias_p3,
         "elegibleili"=elegibleili_p3, "elegibleili7"=elegibleili7dias_p3,
         "elegibleneumonia"=elegibleneumonia_p3, "elegibleneumonia7"=elegibleneumonia7dias_p3,
         "enfermedadaun"=enfermedadaun_p3,
         "consentimientorecibio"=consentimientorecibio_p3,
         "asentimientorecibio"=asentimientorecibio_p3) %>%
   mutate(IDPersona= paste0(id_record,"-03"))

P4Sel <- P4 %>%
  dplyr::filter(!is.na(codigoentrevista_p4))%>%
   select(id_record, "municipio"=municipio_p4, "municipio_des"=municipio_p4_des,
         "cluster"=cluster_p4, "codigovivienda"=codigovivienda_p4,
         "fechaintento1"=fechaintento1_p4, "participacioninvita"=participacioninvita_p4,
         "elegiblefebril"=elegiblefebril_p4, "elegiblefebril7"=elegiblefebril7dias_p4,
         "elegiblediarrea"=elegiblediarrea_p4, "elegiblediarrea7"=elegiblediarrea7dias_p4,
         "elegibleili"=elegibleili_p4, "elegibleili7"=elegibleili7dias_p4,
         "elegibleneumonia"=elegibleneumonia_p4, "elegibleneumonia7"=elegibleneumonia7dias_p4,
         "enfermedadaun"=enfermedadaun_p4,
         "consentimientorecibio"=consentimientorecibio_p4,
         "asentimientorecibio"=asentimientorecibio_p4) %>%
   mutate(IDPersona= paste0(id_record,"-04")) 

P5Sel <- P5 %>% 
  dplyr::filter(!is.na(codigoentrevista_p5)) %>% 
     select(id_record, "municipio"=municipio_p5, "municipio_des"=municipio_p5_des,
            "cluster"=cluster_p5, "codigovivienda"=codigovivienda_p5,
            "fechaintento1"=fechaintento1_p5, "participacioninvita"=participacioninvita_p5,
            "elegiblefebril"=elegiblefebril_p5, "elegiblefebril7"=elegiblefebril7dias_p5,
            "elegiblediarrea"=elegiblediarrea_p5, "elegiblediarrea7"=elegiblediarrea7dias_p5,
            "elegibleili"=elegibleili_p5, "elegibleili7"=elegibleili7dias_p5,
            "elegibleneumonia"=elegibleneumonia_p5, "elegibleneumonia7"=elegibleneumonia7dias_p5,
            "enfermedadaun"=enfermedadaun_p5,
         "consentimientorecibio"=consentimientorecibio_p5,
         "asentimientorecibio"=asentimientorecibio_p5) %>%
   mutate(IDPersona= paste0(id_record,"-05")) 

P6Sel <- P6 %>%
  dplyr::filter(!is.na(codigoentrevista_p6)) %>% 
  select(id_record, "municipio"=municipio_p6, "municipio_des"=municipio_p6_des,
         "cluster"=cluster_p6, "codigovivienda"=codigovivienda_p6,
         "fechaintento1"=fechaintento1_p6, "participacioninvita"=participacioninvita_p6,
         "elegiblefebril"=elegiblefebril_p6, "elegiblefebril7"=elegiblefebril7dias_p6,
         "elegiblediarrea"=elegiblediarrea_p6, "elegiblediarrea7"=elegiblediarrea7dias_p6,
         "elegibleili"=elegibleili_p6, "elegibleili7"=elegibleili7dias_p6,
         "elegibleneumonia"=elegibleneumonia_p6, "elegibleneumonia7"=elegibleneumonia7dias_p6,
         "enfermedadaun"=enfermedadaun_p6,
         "consentimientorecibio"=consentimientorecibio_p6,
         "asentimientorecibio"=asentimientorecibio_p6) %>%
   mutate(IDPersona= paste0(id_record,"-06")) 

P7Sel <- P7 %>%
  dplyr::filter(!is.na(codigoentrevista_p7)) %>% 
  select(id_record, "municipio"=municipio_p7, "municipio_des"=municipio_p7_des,
         "cluster"=cluster_p7, "codigovivienda"=codigovivienda_p7,
         "fechaintento1"=fechaintento1_p7, "participacioninvita"=participacioninvita_p7,
         "elegiblefebril"=elegiblefebril_p7, "elegiblefebril7"=elegiblefebril7dias_p7,
         "elegiblediarrea"=elegiblediarrea_p7, "elegiblediarrea7"=elegiblediarrea7dias_p7,
         "elegibleili"=elegibleili_p7, "elegibleili7"=elegibleili7dias_p7,
         "elegibleneumonia"=elegibleneumonia_p7, "elegibleneumonia7"=elegibleneumonia7dias_p7,
         "enfermedadaun"=enfermedadaun_p7,
         "consentimientorecibio"=consentimientorecibio_p7,
         "asentimientorecibio"=asentimientorecibio_p7) %>%
  mutate(IDPersona= paste0(id_record,"-07")) 

P8Sel <- P8 %>% 
  dplyr::filter(!is.na(codigoentrevista_p8)) %>% 
  select(id_record, "municipio"=municipio_p8, "municipio_des"=municipio_p8_des,
         "cluster"=cluster_p8, "codigovivienda"=codigovivienda_p8,
         "fechaintento1"=fechaintento1_p8, "participacioninvita"=participacioninvita_p8,
         "elegiblefebril"=elegiblefebril_p8, "elegiblefebril7"=elegiblefebril7dias_p8,
         "elegiblediarrea"=elegiblediarrea_p8, "elegiblediarrea7"=elegiblediarrea7dias_p8,
         "elegibleili"=elegibleili_p8, "elegibleili7"=elegibleili7dias_p8,
         "elegibleneumonia"=elegibleneumonia_p8, "elegibleneumonia7"=elegibleneumonia7dias_p8,
         "enfermedadaun"=enfermedadaun_p8,
         "consentimientorecibio"=consentimientorecibio_p8,
         "asentimientorecibio"=asentimientorecibio_p8) %>%
  mutate(IDPersona= paste0(id_record,"-08")) 

P9Sel <- P9 %>%
  dplyr::filter(!is.na(codigoentrevista_p9))%>% 
  select(id_record, "municipio"=municipio_p9, "municipio_des"=municipio_p9_des,
         "cluster"=cluster_p9, "codigovivienda"=codigovivienda_p9,
         "fechaintento1"=fechaintento1_p9, "participacioninvita"=participacioninvita_p9,
         "elegiblefebril"=elegiblefebril_p9, "elegiblefebril7"=elegiblefebril7dias_p9,
         "elegiblediarrea"=elegiblediarrea_p9, "elegiblediarrea7"=elegiblediarrea7dias_p9,
         "elegibleili"=elegibleili_p9, "elegibleili7"=elegibleili7dias_p9,
         "elegibleneumonia"=elegibleneumonia_p9, "elegibleneumonia7"=elegibleneumonia7dias_p9,
         "enfermedadaun"=enfermedadaun_p9,
         "consentimientorecibio"=consentimientorecibio_p9,
         "asentimientorecibio"=asentimientorecibio_p9) %>%
  mutate(IDPersona= paste0(id_record,"-09")) 

P10Sel <- P10 %>%
  dplyr::filter(!is.na(codigoentrevista_p10))%>%
   select(id_record, "municipio"=municipio_p10, "municipio_des"=municipio_p10_des,
         "cluster"=cluster_p10, "codigovivienda"=codigovivienda_p10,
         "fechaintento1"=fechaintento1_p10, "participacioninvita"=participacioninvita_p10,
         "elegiblefebril"=elegiblefebril_p10, "elegiblefebril7"=elegiblefebril7dias_p10,
         "elegiblediarrea"=elegiblediarrea_p10, "elegiblediarrea7"=elegiblediarrea7dias_p10,
         "elegibleili"=elegibleili_p10, "elegibleili7"=elegibleili7dias_p10,
         "elegibleneumonia"=elegibleneumonia_p10, "elegibleneumonia7"=elegibleneumonia7dias_p10,
         "enfermedadaun"=enfermedadaun_p10,
         "consentimientorecibio"=consentimientorecibio_p10,
         "asentimientorecibio"=asentimientorecibio_p10) %>%
   mutate(IDPersona= paste0(id_record,"-10")) 

P11Sel <- P11 %>%
  dplyr::filter(!is.na(codigoentrevista_p11))%>%
   select(id_record, "municipio"=municipio_p11, "municipio_des"=municipio_p11_des,
         "cluster"=cluster_p11, "codigovivienda"=codigovivienda_p11,
         "fechaintento1"=fechaintento1_p11, "participacioninvita"=participacioninvita_p11,
         "elegiblefebril"=elegiblefebril_p11, "elegiblefebril7"=elegiblefebril7dias_p11,
         "elegiblediarrea"=elegiblediarrea_p11, "elegiblediarrea7"=elegiblediarrea7dias_p11,
         "elegibleili"=elegibleili_p11, "elegibleili7"=elegibleili7dias_p11,
         "elegibleneumonia"=elegibleneumonia_p11, "elegibleneumonia7"=elegibleneumonia7dias_p11,
         "enfermedadaun"=enfermedadaun_p11,
         "consentimientorecibio"=consentimientorecibio_p11,
         "asentimientorecibio"=asentimientorecibio_p11) %>%
   mutate(IDPersona= paste0(id_record,"-11")) 

P12Sel <- P12 %>%
  dplyr::filter(!is.na(codigoentrevista_p12))%>%
   select(id_record, "municipio"=municipio_p12, "municipio_des"=municipio_p12_des,
         "cluster"=cluster_p12, "codigovivienda"=codigovivienda_p12,
         "fechaintento1"=fechaintento1_p12, "participacioninvita"=participacioninvita_p12,
         "elegiblefebril"=elegiblefebril_p12, "elegiblefebril7"=elegiblefebril7dias_p12,
         "elegiblediarrea"=elegiblediarrea_p12, "elegiblediarrea7"=elegiblediarrea7dias_p12,
         "elegibleili"=elegibleili_p12, "elegibleili7"=elegibleili7dias_p12,
         "elegibleneumonia"=elegibleneumonia_p12, "elegibleneumonia7"=elegibleneumonia7dias_p12,
         "enfermedadaun"=enfermedadaun_p12,
         "consentimientorecibio"=consentimientorecibio_p12,
         "asentimientorecibio"=asentimientorecibio_p12) %>%
   mutate(IDPersona= paste0(id_record,"-12")) 

P13Sel <- P13 %>%
  dplyr::filter(!is.na(codigoentrevista_p13)) %>%
   select(id_record, "municipio"=municipio_p13, "municipio_des"=municipio_p13_des,
         "cluster"=cluster_p13, "codigovivienda"=codigovivienda_p13,
         "fechaintento1"=fechaintento1_p13, "participacioninvita"=participacioninvita_p13,
         "elegiblefebril"=elegiblefebril_p13, "elegiblefebril7"=elegiblefebril7dias_p13,
         "elegiblediarrea"=elegiblediarrea_p13, "elegiblediarrea7"=elegiblediarrea7dias_p13,
         "elegibleili"=elegibleili_p13, "elegibleili7"=elegibleili7dias_p13,
         "elegibleneumonia"=elegibleneumonia_p13, "elegibleneumonia7"=elegibleneumonia7dias_p13,
         "enfermedadaun"=enfermedadaun_p13,
         "consentimientorecibio"=consentimientorecibio_p13,
         "asentimientorecibio"=asentimientorecibio_p13) %>%
   mutate(IDPersona= paste0(id_record,"-13")) 

P14Sel <- P14 %>%
  dplyr::filter(!is.na(codigoentrevista_p14)) %>%
   select(id_record, "municipio"=municipio_p14, "municipio_des"=municipio_p14_des,
         "cluster"=cluster_p14, "codigovivienda"=codigovivienda_p14,
         "fechaintento1"=fechaintento1_p14, "participacioninvita"=participacioninvita_p14,
         "elegiblefebril"=elegiblefebril_p14, "elegiblefebril7"=elegiblefebril7dias_p14,
         "elegiblediarrea"=elegiblediarrea_p14, "elegiblediarrea7"=elegiblediarrea7dias_p14,
         "elegibleili"=elegibleili_p14, "elegibleili7"=elegibleili7dias_p14,
         "elegibleneumonia"=elegibleneumonia_p14, "elegibleneumonia7"=elegibleneumonia7dias_p14,
         "enfermedadaun"=enfermedadaun_p14,
         "consentimientorecibio"=consentimientorecibio_p14,
         "asentimientorecibio"=asentimientorecibio_p14) %>%
   mutate(IDPersona= paste0(id_record,"-14")) 


P15Sel <- P15 %>%
  dplyr::filter(!is.na(codigoentrevista_p15))%>%
  select(id_record, "municipio"=municipio_p15, "municipio_des"=municipio_p15_des,
         "cluster"=cluster_p15, "codigovivienda"=codigovivienda_p15,
         "fechaintento1"=fechaintento1_p15, "participacioninvita"=participacioninvita_p15,
         "elegiblefebril"=elegiblefebril_p15, "elegiblefebril7"=elegiblefebril7dias_p15,
         "elegiblediarrea"=elegiblediarrea_p15, "elegiblediarrea7"=elegiblediarrea7dias_p15,
         "elegibleili"=elegibleili_p15, "elegibleili7"=elegibleili7dias_p15,
         "elegibleneumonia"=elegibleneumonia_p15, "elegibleneumonia7"=elegibleneumonia7dias_p15,
         "enfermedadaun"=enfermedadaun_p15,
         "consentimientorecibio"=consentimientorecibio_p15,
         "asentimientorecibio"=asentimientorecibio_p15) %>%
   mutate(IDPersona= paste0(id_record,"-15")) 

 
PSel <- rbind(P1Sel, P2Sel, P3Sel, P4Sel, P5Sel, P6Sel, P7Sel, P8Sel, P9Sel, P10Sel, P11Sel, P12Sel, P13Sel, P14Sel, P15Sel)

PTam <- PSel %>%
   dplyr::filter(participacioninvita==1)

 #PTam = persons screened (tamizados) that were invited to participate
```



Cambiar variables
#change variables from 1,2 to 1,0 (0=no)
```{r}
 PTam$elegiblefebril <- replace(PTam$elegiblefebril, which(PTam$elegiblefebril==2),0)
 PTam$elegiblediarrea <- replace(PTam$elegiblediarrea, which(PTam$elegiblediarrea==2),0)
 PTam$elegibleili <- replace(PTam$elegibleili, which(PTam$elegibleili==2),0)
 PTam$elegibleneumonia <- replace(PTam$elegibleneumonia, which(PTam$elegibleneumonia==2),0)
 
 PTam$elegiblefebril7 <- replace(PTam$elegiblefebril7, which(PTam$elegiblefebril7==2),0)
 PTam$elegiblediarrea7 <- replace(PTam$elegiblediarrea7, which(PTam$elegiblediarrea7==2),0)
 PTam$elegibleili7 <- replace(PTam$elegibleili7, which(PTam$elegibleili7==2),0)
 PTam$elegibleneumonia7 <- replace(PTam$elegibleneumonia7, which(PTam$elegibleneumonia7==2),0)
```


Agregar variable de area rural o urbano
```{r}
#RuralUrbano <- clusters %>%
#   merge(clustersVis %>% select(id_record, area, area_des), by.x="IDCluster", by.y="id_record") %>%
#   mutate(NumCluster = as.numeric(substr(IDCluster,2,4))) %>%
#  dplyr::filter(NumCluster<=200) %>%
#select(IDCluster, area, area_des)



#RuralUrbano <- clustersVis  %>%
#   mutate(NumCluster = as.numeric(substr(IDCluster,2,4))) %>%
#  dplyr::filter(NumCluster<=230) %>%
#select(IDCluster, area, area_des)
#the number of clusters may have to change and may be bigger


RuralUrbano <- clustersVis %>%
  select(cluster, area, area_des)

PTam <- PTam %>% merge(RuralUrbano, by.x="cluster")
```


Agregar datos de edad, sexo y educacion
```{r}
 Sexo<- hogaresVis %>%
   select(id_record, sexop1,sexop2,sexop3,sexop4,
   sexop5,sexop6,sexop7,sexop8, sexop9,sexop10,sexop11,sexop12, sexop13,sexop14,sexop15) %>%
   melt(id.vars=c("id_record"),measured.vars=c("sexop1","sexop2","sexop3","sexop4",
                                               "sexop5","sexop6","sexop7","sexop8",
                                               "sexop9","sexop10","sexop11","sexop12",
                                               "sexop13","sexop14","sexop15")) %>%
   mutate(IDPersona = ifelse(nchar(as.character(variable))==6,
                             paste0(id_record, "-0", substr(variable,6,6)),
                             paste0(id_record, "-", substr(variable,6,7)))) %>%
   select(IDPersona, "sexo"=value)
 
Sexo
 
 Sexo_des<- hogaresVis %>%
   select(id_record, sexop1_des,sexop2_des,sexop3_des,sexop4_des,
          sexop5_des,sexop6_des,sexop7_des,sexop8_des, sexop9_des,
          sexop10_des,sexop11_des,sexop12_des, sexop13_des,
          sexop14_des,sexop15_des) %>%
   melt(id.vars=c("id_record"),
        measured.vars=c("sexop1_des","sexop2_des","sexop3_des","sexop4_des",
                        "sexop5_des","sexop6_des","sexop7_des","sexop8_des",
                        "sexop9_des","sexop10_des","sexop11_des","sexop12_des",
                        "sexop13_des","sexop14_des","sexop15_des")) %>%
   mutate(IDPersona = ifelse(nchar(as.character(variable))==10,
                             paste0(id_record, "-0", substr(variable,6,6)),
                             paste0(id_record, "-", substr(variable,6,7)))) %>%
   select(IDPersona, "sexo_des"=value)
 
 Sexo_des
 
 Edad<- hogaresVis %>%
   select(id_record, edadp1,edadp2,edadp3,edadp4,
          edadp5, edadp6, edadp7, edadp8, edadp9,
          edadp10, edadp11, edadp12, edadp13,
          edadp14, edadp15) %>%
   melt(id.vars=c("id_record"),
        measured.vars=c("edadp1","edadp2","edadp3","edadp4",
                        "edadp5","edadp6","edadp7","edadp8",
                        "edadp9","edadp10","edadp11","edadp12",
                        "edadp13","edadp14","edadp15")) %>%
   mutate(IDPersona = ifelse(nchar(as.character(variable))==6,
                             paste0(id_record, "-0", substr(variable,6,6)),
                             paste0(id_record, "-", substr(variable,6,7)))) %>%
   select(IDPersona, "edad"=value) %>%
   mutate(edadnum = as.numeric(as.character(edad)),
          edad5 = ifelse(edadnum<5,1,0)) %>%
   select(-edad)

Educacion<- hogaresVis %>%
   select(id_record, educacionp1,educacionp2,educacionp3,educacionp4,
   educacionp5,educacionp6,educacionp7,educacionp8, educacionp9,
   educacionp10,educacionp11,educacionp12, educacionp13,educacionp14,educacionp15) %>%
   melt(id.vars=c("id_record"),measured.vars=c("educacionp1","educacionp2","educacionp3","educacionp4",
                                               "educacionp5","educacionp6","educacionp7","educacionp8",
                                               "educacionp9","educacionp10","educacionp11","educacionp12",
                                               "educacionp13","educacionp14","educacionp15")) %>%
   mutate(IDPersona = ifelse(nchar(as.character(variable))==11,
                             paste0(id_record, "-0", substr(variable,11,11)),
                             paste0(id_record, "-", substr(variable,11,12)))) %>%
   select(IDPersona, "educacion"=value)
 
Educacion


 PTam <- PTam %>%
   merge(Sexo, by="IDPersona") %>%
   merge(Sexo_des, by="IDPersona") %>%
   merge(Edad, by="IDPersona") %>%
   merge(Educacion, by="IDPersona")
```



# 4. Establecer pesos para PTam, the code should generate numbers
GK_total_pop
gk
nk_psu_sel
# need to change the NumCluster to include the total number of clusters included in the tamizaje

Pesos de seleccion de los clusters
```{r}
# Gk is the estimated total population in stratum k (the total population in the catchment area)
Gk_total_pop <- clusters$str_pop[1]
Gk_total_pop

# gik is the estimated population in PSU (primary sampling unit, cluster) i in stratum k

gk <- clusters %>% 
  select(TipoCluster,IDCluster, "gik_psu_pop"=psu_pop)%>%
  dplyr::filter(TipoCluster=="WT")

gk

# nk is the number of selected PSUs(primary sampling unit, cluster) in stratum k
nk_psu_sel <- clustersVis %>%
  mutate(NumCluster = as.numeric(substr(cluster,2,4))) %>%
  dplyr::filter(NumCluster>=230) %>% 
  distinct(cluster) %>% 
  n_distinct()
nk_psu_sel


# Agregar datos
PTam <- PTam %>% 
  mutate(Gk_total_pop = Gk_total_pop) %>%
  merge(gk, by.x = "cluster", by.y="IDCluster", all.x = T)%>% 
  mutate(nk_psu_sel = nk_psu_sel)%>% 
  mutate(ClusterSelectionWeight = (Gk_total_pop / as.numeric(gik_psu_pop))/nk_psu_sel) #each cluster will have their own cluster selection weight, this is a selection weight

head(PTam)

```


Pesos de seleccion por vivienda
```{r}
# Mik is the number of total households enumerated in PSUi and stratum k (all households that existed)

Mk <- hogaresWT_n %>% 
  mutate(NCluster = as.numeric(substr(cluster,2,4))) %>%
  dplyr::filter(NCluster >= 230) %>%
  group_by(cluster) %>% 
  count() %>%
  dplyr::rename("Mik_house_total" = n)

Mk

# mik is the number of households selected in PSUi and stratum k (all of the houses that were selected)
#for wellcome trust, used hogaresWT_n from chunks above
mk <- hogaresWT_n %>% 
  group_by(cluster) %>% 
  count() %>%
  dplyr::rename("mik_house_sel" = n)

mk

PTam <- PTam %>% 
  merge(Mk, by = "cluster", all.x = T) %>% 
  merge(mk, by = "cluster", all.x = T) %>%
  mutate(HouseholdSelectionWeight = Mik_house_total/mik_house_sel) #this is the weight for household selection within the cluster, the number is the same for each cluster

head(PTam) #show me the first 10 lines

```



Peso de seleccion por individuo, for wellcome trust, only the children in the household are counted as individuals enumerated
```{r}
# Uijk is the number of total individuals enumerated in household j, PSU i and stratum k

hogaresVis$edadp1 <- as.numeric(hogaresVis$edadp1)
hogaresVis$edadp2 <- as.numeric(hogaresVis$edadp2)
hogaresVis$edadp3 <- as.numeric(hogaresVis$edadp3)
hogaresVis$edadp4 <- as.numeric(hogaresVis$edadp4)
hogaresVis$edadp5 <- as.numeric(hogaresVis$edadp5)
hogaresVis$edadp6 <- as.numeric(hogaresVis$edadp6)
hogaresVis$edadp7 <- as.numeric(hogaresVis$edadp7)
hogaresVis$edadp8 <- as.numeric(hogaresVis$edadp8)
hogaresVis$edadp9 <- as.numeric(hogaresVis$edadp9)
hogaresVis$edadp10 <- as.numeric(hogaresVis$edadp10)
hogaresVis$edadp11 <- as.numeric(hogaresVis$edadp11)
hogaresVis$edadp12 <- as.numeric(hogaresVis$edadp12)
hogaresVis$edadp13 <- as.numeric(hogaresVis$edadp13)
hogaresVis$edadp14 <- as.numeric(hogaresVis$edadp14)
hogaresVis$edadp15 <- as.numeric(hogaresVis$edadp15)

Uk <- hogaresVis %>% 
  dplyr::filter(participa==1) %>%
  mutate(HayP1 = ifelse(!is.na(nombrep1)& edadp1<15,1,0),
         HayP2 = ifelse(!is.na(nombrep2)& edadp2<15,1,0),
         HayP3 = ifelse(!is.na(nombrep3)& edadp3<15,1,0),
         HayP4 = ifelse(!is.na(nombrep4)& edadp4<15,1,0),
         HayP5 = ifelse(!is.na(nombrep5)& edadp5<15,1,0),
         HayP6 = ifelse(!is.na(nombrep6)& edadp6<15,1,0),
         HayP7 = ifelse(!is.na(nombrep7)& edadp7<15,1,0),
         HayP8 = ifelse(!is.na(nombrep8)& edadp8<15,1,0),
         HayP9 = ifelse(!is.na(nombrep9)& edadp9<15,1,0),
         HayP10 = ifelse(!is.na(nombrep10)& edadp10<15,1,0),
         HayP11 = ifelse(!is.na(nombrep11)& edadp11<15,1,0),
         HayP12 = ifelse(!is.na(nombrep12)& edadp12<15,1,0),
         HayP13 = ifelse(!is.na(nombrep13)& edadp13<15,1,0),
         HayP14 = ifelse(!is.na(nombrep14)& edadp14<15,1,0),
         HayP15 = ifelse(!is.na(nombrep15)& edadp15<15,1,0)) %>%
  select(id_record, HayP1, HayP2, HayP3, HayP4, HayP5, HayP6, HayP7, HayP8, HayP9, HayP10, HayP11, HayP12, HayP13, HayP14, HayP15) %>%
  mutate(Uijk_ind_total = rowSums(.[,-1])) %>%
  select(id_record, (Uijk_ind_total))

head(Uk)

# uijk is the number of selected individuals enumerated in household j, PSU i and stratum k
uk <- PSel %>%
  group_by(id_record) %>%
  count() %>%
  dplyr::rename("uijk_ind_sel" = n)

uk

PTam <- PTam %>% 
  merge(Uk, by = "id_record", all.x = T) %>% 
  merge(uk, by = "id_record", all.x = T) %>%
  mutate(IndividualSelectionWeight = Uijk_ind_total/uijk_ind_sel) %>%
  mutate(SelectionWeight_indLevel = ClusterSelectionWeight*HouseholdSelectionWeight*IndividualSelectionWeight,
         SelectionWeight_houseLevel = ClusterSelectionWeight*HouseholdSelectionWeight)

head(PTam) #show me the first 10 lines
```


Peso de respuesta por cluster


```{r}
# nk is the number of selected PSUs in stratum k
PTam$nk_psu_sel

# nkx is the number of found and sampled PSUs in stratum k
nkx_PSU_enr <- PTam %>% distinct(cluster) %>% n_distinct()
nkx_PSU_enr

PTam <- PTam %>%
  mutate(nkx_PSU_enr = nkx_PSU_enr) %>%
  mutate(ClusterResponseWeight = nk_psu_sel/nkx_PSU_enr)

head(PTam)
```

Peso de respuesta por casa
```{r}
#mik is the number of selected household in PSUi and statum k
PTam$mik_house_sel

# mikx is the number of found and responded households in PSUi and statum k
mkx <- hogaresVis %>%
  dplyr::filter(participa==1) %>%
  group_by(cluster) %>%
  count() %>%
  dplyr::rename("mikx_house_enr"=n)
mkx

PTam <- PTam %>% 
  merge(mkx, by="cluster") %>%
  mutate(HouseResponseWeight = mik_house_sel/mikx_house_enr) 
  
head(PTam)
```

Peso de respuesta por individuo
```{r}
#uijk is the number of selected persons in household j, PSUi and statum k
PTam$uijk_ind_sel

# uijkx is the number of found and responded individuals in household j, PSUi and statum k
uijkx <- PTam %>%
  filter(consentimientorecibio==1) %>% ### 2025 sep 30: Agregue esta condicion porque si no hay mas de un nino por casa. LMG. 
  group_by(id_record) %>%
  count() %>%
  dplyr::rename("uijkx_ind_enr"=n)
uijkx

PTam <- PTam %>% 
  merge(uijkx, by="id_record") %>%
  mutate(IndividualResponseWeight = uijk_ind_sel/uijkx_ind_enr) %>%
  mutate(ResponseWeight_indLevel = ClusterResponseWeight*HouseResponseWeight*IndividualResponseWeight,
 ResponseWeight_houseLevel = ClusterResponseWeight*HouseResponseWeight) %>%
mutate(Weights_indLevel = SelectionWeight_indLevel * ResponseWeight_indLevel,
        Weights_houseLevel = SelectionWeight_houseLevel * ResponseWeight_houseLevel) %>%
  filter(TipoCluster=="WT")
  
  
head(PTam)
```


## Summary


```{r}
# 2025 sep 30
# Hay clusters que se usaron mas de una vez. si no divido por el numero de veces que se usa un cluster, estoy sobreestimando
NumClusters <- PTam %>% 
  count(cluster); NumClusters

# Numero de casas que se usaron mas de una vez
NumHouseholds <- PTam %>% 
  filter(consentimientorecibio==1) %>% 
  count(id_record) %>% 
  select(id_record, "n2"=n); NumHouseholds
NumHouseholds %>% arrange(desc(n2))

# Individuos
NumIndividuals <- PTam %>% 
  count(IDPersona) %>% 
  select(IDPersona, "n3"=n); 
NumIndividuals %>% arrange(desc(n3))



PTam <-   PTam %>% 
  merge(NumClusters, by="cluster") %>% 
  merge(NumHouseholds, by="id_record") %>% 
  rowwise() %>% 
  mutate(WeightCluster = ClusterSelectionWeight*ClusterResponseWeight/n, # 2025 sep 30: Agregue esta condicion sino los pesos se duplican.
         WeightHouse = HouseholdSelectionWeight*HouseResponseWeight/n2,
         WeightInd = IndividualSelectionWeight*IndividualResponseWeight,
         Weight = WeightCluster*WeightHouse*WeightInd) 

#*ClusterResponseWeight
#*

```


Check clusters
```{r}
PTam %>% 
  select(cluster,id_record,IDPersona, 
         Gk_total_pop, gik_psu_pop, nk_psu_sel, ClusterSelectionWeight,
         nk_psu_sel, nkx_PSU_enr, ClusterResponseWeight, 
         n, WeightCluster)

sum(PTam$WeightCluster)
```


Check households
```{r}
PTam %>% 
  select(cluster,id_record,IDPersona,
         Mik_house_total, mik_house_sel, HouseholdSelectionWeight,
         mik_house_sel, mikx_house_enr, HouseResponseWeight, WeightHouse)
sum(PTam$WeightHouse)

```

Check individuals
```{r}
PTam %>% 
  select(cluster,id_record,IDPersona,
         Uijk_ind_total, uijk_ind_sel, IndividualSelectionWeight,
         uijk_ind_sel, uijkx_ind_enr, IndividualResponseWeight, WeightInd) 

sum(PTam$WeightInd)

```




# 5. Guardar datos

```{r}
write_rds(PTam, "Tabla de tamizados con pesos_WT_BR.rds")
```







