---
title: "Description of Healthcare utilization practices"
author: "Laura Grajeda"
date: "2026-04-22"
output: html_document
---




```{r include=FALSE}
library(tidyverse)
library(survey)
library(compareGroups)
library(readxl)
library(here)
```


# 1. Goal

Describe health care utilization

# 2. Datos

```{r}
PTam <- readRDS(here("1_Create_dataset","output", "HUS_Dataset.rds")) 
Censo <- readRDS(here("1_Create_dataset","output", "Population_Totals_CensusDataset.rds")) 
```




# 3. Variables


## + Syndromes
```{r}
# Numeric
PTam$elegibleneumonia_num <- as.numeric(PTam$elegibleneumonia)
PTam$elegibleili_num <- as.numeric(PTam$elegibleili)
PTam$elegiblefebril_FUO_num <- as.numeric(PTam$elegiblefebril_FUO)
PTam$elegiblediarrea_num <- as.numeric(PTam$elegiblediarrea)


# Binary
PTam$elegiblefebril_FUO <- factor(PTam$elegiblefebril_FUO, levels = c(1,0), labels = c("Si", "No"))
PTam$elegiblefebril7_FUO <- factor(PTam$elegiblefebril7_FUO, levels = c(1,0), labels = c("Si", "No"))
PTam$elegibleili <- factor(PTam$elegibleili, levels = c(1,0), labels = c("Si", "No"))
PTam$elegibleili7 <- factor(PTam$elegibleili7, levels = c(1,0), labels = c("Si", "No"))
PTam$elegiblediarrea <- factor(PTam$elegiblediarrea, levels = c(1,0), labels = c("Si", "No"))
PTam$elegiblediarrea7 <- factor(PTam$elegiblediarrea7, levels = c(1,0), labels = c("Si", "No"))
PTam$elegibleneumonia <- factor(PTam$elegibleneumonia, levels = c(1,0), labels = c("Si", "No"))
```



## + Sought healthcare
```{r}
# For ILI, diarrhea, and FUO
PTam %>% count(buscoayuda)
PTam$buscoayuda <- as.numeric(PTam$buscoayuda)
PTam$buscoayuda_des <- factor(PTam$buscoayuda, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$buscoayuda_des, "label")<- "Sought care"

# For pneumonia
PTam$neumopaayuda <- as.numeric(PTam$neumopaayuda)
PTam$neumopaayuda_des <- factor(PTam$neumopaayuda, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$neumopaayuda_des, "label")<- "Sought care"
```


## + Places of healthcare seeking

Place public
```{r}
PTam <- PTam %>% 
  mutate(Publico = ifelse(ClinicaPublica==1 | HospitalPublico==1,1,0),
         PublicoPneumo = ifelse(ClinicaPublicaPneumo==1 | HospitalPublicaPneumo==1,1,0))

PTam$Publico <- as.numeric(PTam$Publico)
PTam$Publico_des <- factor(PTam$Publico, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$Publico_des, "label")<- "Public facility (clinic or hospital)"

PTam$PublicoPneumo <- as.numeric(PTam$PublicoPneumo)
PTam$PublicoPneumo_des <- factor(PTam$PublicoPneumo, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$PublicoPneumo_des, "label")<- "Public facility (clinic or hospital)"

```


Lugar especifico
```{r}
# Farmacia-tienda
#-----------------
PTam$FarmaciaTienda <- as.numeric(PTam$FarmaciaTienda)
PTam$FarmaciaTienda_des <- factor(PTam$FarmaciaTienda, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$FarmaciaTienda_des, "label")<- "Pharmacy or corner store"

PTam$FarmaciaTiendaPneumo <- as.numeric(PTam$FarmaciaTiendaPneumo)
PTam$FarmaciaTiendaPneumo_des <- factor(PTam$FarmaciaTiendaPneumo, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$FarmaciaTiendaPneumo_des, "label")<- "Pharmacy or corner store"


# Tradicional
#-----------------
PTam$Tradicional <- as.numeric(PTam$Tradicional)
PTam$Tradicional_des <- factor(PTam$Tradicional, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$Tradicional_des, "label")<- "Traditional care"

PTam$TradicionalPneumo <- as.numeric(PTam$TradicionalPneumo)
PTam$TradicionalPneumo_des <- factor(PTam$TradicionalPneumo, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$TradicionalPneumo_des, "label")<- "Traditional care"


# Clinica publica
#-----------------
PTam$ClinicaPublica <- as.numeric(PTam$ClinicaPublica)
PTam$ClinicaPublica_des <- factor(PTam$ClinicaPublica, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$ClinicaPublica_des, "label")<- "Public clinic"

PTam$ClinicaPublicaPneumo <- as.numeric(PTam$ClinicaPublicaPneumo)
PTam$ClinicaPublicaPneumo_des <- factor(PTam$ClinicaPublicaPneumo, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$ClinicaPublicaPneumo_des, "label")<- "Public clinic"


# Clinica privada
#-----------------
PTam$ClinicaPrivada <- as.numeric(PTam$ClinicaPrivada)
PTam$ClinicaPrivada_des <- factor(PTam$ClinicaPrivada, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$ClinicaPrivada_des, "label")<- "Private clinic"

PTam$ClinicaPrivadaPneumo <- as.numeric(PTam$ClinicaPrivadaPneumo)
PTam$ClinicaPrivadaPneumo_des <- factor(PTam$ClinicaPrivadaPneumo, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$ClinicaPrivadaPneumo_des, "label")<- "Private clinic"



# Seguro social
#-----------------
PTam$ClinicaSeguroSocial <- as.numeric(PTam$ClinicaSeguroSocial)
PTam$ClinicaSeguroSocial_des <- factor(PTam$ClinicaSeguroSocial, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$ClinicaSeguroSocial_des, "label")<- "Social security clinic"

PTam$ClinicaSeguroSocialPneumo <- as.numeric(PTam$ClinicaSeguroSocialPneumo)
PTam$ClinicaSeguroSocialPneumo_des <- factor(PTam$ClinicaSeguroSocialPneumo, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$ClinicaSeguroSocialPneumo_des, "label")<- "Social security clinic"



# Hospital publico
#-----------------
PTam$HospitalPublico <- as.numeric(PTam$HospitalPublico)
PTam$HospitalPublico_des <- factor(PTam$HospitalPublico, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$HospitalPublico_des, "label")<- "Public hospital"

PTam$HospitalPublicaPneumo <- as.numeric(PTam$HospitalPublicaPneumo)
PTam$HospitalPublicaPneumo_des <- factor(PTam$HospitalPublicaPneumo, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$HospitalPublicaPneumo_des, "label")<- "Public hospital"


# Hospital privado
#-----------------
PTam$HospitalPrivado <- as.numeric(PTam$HospitalPrivado)
PTam$HospitalPrivado_des <- factor(PTam$HospitalPrivado, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$HospitalPrivado_des, "label")<- "Private hospital"

PTam$HospitalPrivadoPneumo <- as.numeric(PTam$HospitalPrivadoPneumo)
PTam$HospitalPrivadoPneumo_des <- factor(PTam$HospitalPrivadoPneumo, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$HospitalPrivadoPneumo_des, "label")<- "Private hospital"
```



## + Antibiotic use
```{r}
# Uso de anntibiotico
#-----------------
PTam$Antibiotico <- as.numeric(PTam$Antibiotico)
PTam$Antibiotico_des <- factor(PTam$Antibiotico, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$Antibiotico_des, "label")<- "Antibiotic use"

PTam$AntibioticoPneumo <- as.numeric(PTam$AntibioticoPneumo)
PTam$AntibioticoPneumo_des <- factor(PTam$AntibioticoPneumo, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$AntibioticoPneumo_des, "label")<- "Antibiotic use"


# Uso de antibiotico autorecetado
#-----------------
PTam$AntibioticoSelf <- as.numeric(PTam$AntibioticoSelf)
PTam$AntibioticoSelf_des <- factor(PTam$AntibioticoSelf, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$AntibioticoSelf_des, "label")<- "Antibiotic use - self medicated"

PTam$AntibioticoPneumoSelf <- as.numeric(PTam$AntibioticoPneumoSelf)
PTam$AntibioticoPneumoSelf_des <- factor(PTam$AntibioticoPneumoSelf, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$AntibioticoPneumoSelf_des, "label")<- "Antibiotic use - self medicated"


# Antibiotico especifico utilizado
#-----------------
PTam <- PTam %>% 
  mutate(
    AntibioticoCual_des = case_when(
      Antibiotico==0 ~ "None",
      !is.na(AntibioticoCual) ~ AntibioticoCual),
    
    AntibioticoCualPneumo_des = case_when(
      AntibioticoPneumo==0 ~ "None",
      !is.na(AntibioticoCualPneumo) ~ AntibioticoCualPneumo))

PTam$AntibioticoCual_des <- factor(PTam$AntibioticoCual_des)
attr(PTam$AntibioticoCual_des, "label")<- "Antibiotic which"

PTam$AntibioticoCualPenumo_des <- factor(PTam$AntibioticoCualPneumo_des)
attr(PTam$AntibioticoCualPneumo_des, "label")<- "Antibiotic which"



# Clase de antibiotico utilizado 
# #-----------------
PTam <- PTam %>% 
  mutate(
    AntibioticoClase_des = case_when(
      Antibiotico==0 ~ "None",
      !is.na(AntibioticoClase) ~ AntibioticoClase),
    AntibioticoClasePneumo_des = case_when(
      AntibioticoPneumo==0 ~ "None",
      !is.na(AntibioticoClasePneumo) ~ AntibioticoClasePneumo),
    
    BLactam = case_when(
      AntibioticoClase_des=="B-Lactams" ~ 1,
      AntibioticoClase_des!="B-Lactams" ~ 0,
      Antibiotico==0 ~ 0),
    BLactamPneumo = case_when(
      AntibioticoClasePneumo_des=="B-Lactams" ~ 1,
      AntibioticoClasePneumo_des=="B-Lactams and Tetracyclins" ~ 1,
      AntibioticoClasePneumo_des!="B-Lactams" ~ 0,
      AntibioticoPneumo==0 ~ 0),
    
    Tetracyclins = case_when(
      AntibioticoClase_des=="Tetracyclins" ~ 1,
      AntibioticoClase_des!="Tetracyclins" ~ 0,
      Antibiotico==0 ~ 0),
    TetracyclinsPneumo = case_when(
      AntibioticoClasePneumo_des=="Tetracyclins" ~ 1,
      AntibioticoClasePneumo_des=="B-Lactams and Tetracyclins" ~ 1,
      AntibioticoClasePneumo_des!="Tetracyclins" ~ 0,
      AntibioticoPneumo==0 ~ 0),
    
    Sulfonamides = case_when(
      AntibioticoClase_des=="Sulfonamides" ~ 1,
      AntibioticoClase_des!="Sulfonamides" ~ 0,
      Antibiotico==0 ~ 0),
    
    Macrolides = case_when(
      AntibioticoClase_des=="Macrolides" ~ 1,
      AntibioticoClase_des!="Macrolides" ~ 0,
      Antibiotico==0 ~ 0),
    MacrolidesPneumo = case_when(
      AntibioticoClasePneumo_des=="Macrolides" ~ 1,
      AntibioticoClasePneumo_des!="Macrolides" ~ 0,
      AntibioticoPneumo==0 ~ 0),
    
    Lincosamides = case_when(
      AntibioticoClase_des=="Lincosamide" ~ 1,
      AntibioticoClase_des!="Lincosamide" ~ 0,
      Antibiotico==0 ~ 0),
    LincosamidesPneumo = case_when(
      AntibioticoClasePneumo_des=="Lincosamide" ~ 1,
      AntibioticoClasePneumo_des!="Lincosamide" ~ 0,
      AntibioticoPneumo==0 ~ 0),
    
    Nitroimidazoles = case_when(
      AntibioticoClase_des=="Nitroimidazoles" ~ 1,
      AntibioticoClase_des!="Nitroimidazoles" ~ 0,
      Antibiotico==0 ~ 0),
    Unknown = case_when(
      AntibioticoClase_des=="Unknown" ~ 1,
      AntibioticoClase_des!="Unknown" ~ 0,
      Antibiotico==0 ~ 0))

PTam$AntibioticoClase_des <- factor(PTam$AntibioticoClase_des, 
          levels = c("B-Lactams", "Tetracyclins", "Sulfonamides", "Macrolides", 
                     "Lincosamide", "Nitroimidazoles", "Unknown", "None"))
attr(PTam$AntibioticoClase_des, "label")<- "Antibiotic type"


# Lactams
#-----------------
PTam$BLactam <- as.numeric(PTam$BLactam)
PTam$BLactam_des <- factor(PTam$BLactam, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$BLactam_des, "label")<- "B-Lactams"

PTam$BLactamPneumo <- as.numeric(PTam$BLactamPneumo)
PTam$BLactamPneumo_des <- factor(PTam$BLactamPneumo, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$BLactamPneumo_des, "label")<- "B-Lactams"

# Tetracyclins
#-----------------
PTam$Tetracyclins <- as.numeric(PTam$Tetracyclins)
PTam$Tetracyclins_des <- factor(PTam$Tetracyclins, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$Tetracyclins_des, "label")<- "Tetracyclins"

PTam$TetracyclinsPneumo <- as.numeric(PTam$TetracyclinsPneumo)
PTam$TetracyclinsPneumo_des <- factor(PTam$TetracyclinsPneumo, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$TetracyclinsPneumo_des, "label")<- "Tetracyclins"

# Macrolides
#-----------------
PTam$Macrolides <- as.numeric(PTam$Macrolides)
PTam$Macrolides_des <- factor(PTam$Macrolides, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$Macrolides_des, "label")<- "Macrolides"

PTam$MacrolidesPneumo <- as.numeric(PTam$MacrolidesPneumo)
PTam$MacrolidesPneumo_des <- factor(PTam$MacrolidesPneumo, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$MacrolidesPneumo_des, "label")<- "Macrolides"

# Lincosamides
#-----------------
PTam$Lincosamides <- as.numeric(PTam$Lincosamides)
PTam$Lincosamides_des <- factor(PTam$Lincosamides, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$Lincosamides_des, "label")<- "Lincosamides"

PTam$LincosamidesPneumo <- as.numeric(PTam$LincosamidesPneumo)
PTam$LincosamidesPneumo_des <- factor(PTam$LincosamidesPneumo, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$LincosamidesPneumo_des, "label")<- "Lincosamides"

```



## + Razons for not seeking care

```{r}
# For pneumonia
PTam$neumoparazon_Nocreyoque1 <- factor(PTam$neumoparazon_Nocreyoque1, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$neumoparazon_Nocreyoque1, "label")<- "Did not think the illness was serious enough"

PTam$neumoparazon_Laclinicae2 <- factor(PTam$neumoparazon_Laclinicae2, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$neumoparazon_Laclinicae2, "label")<- "Healthcare facility was too far from home"

PTam$neumoparazon_Nohubomedi3 <- factor(PTam$neumoparazon_Nohubomedi3, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$neumoparazon_Nohubomedi3, "label")<- "No transportation was available"

PTam$neumoparazon_Noteniadin4 <- factor(PTam$neumoparazon_Noteniadin4, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$neumoparazon_Noteniadin4, "label")<- "Did not have enough money"

PTam$neumoparazon_Nopodiades5 <- factor(PTam$neumoparazon_Nopodiades5, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$neumoparazon_Nopodiades5, "label")<- "Could not leave household responsibilities"

PTam$neumoparazon_Nopodiaaus6 <- factor(PTam$neumoparazon_Nopodiaaus6, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$neumoparazon_Nopodiaaus6, "label")<- "Could not miss work"                     

PTam$neumoparazon_Nosabiaado7 <- factor(PTam$neumoparazon_Nosabiaado7, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$neumoparazon_Nosabiaado7, "label")<- "Did not know where to seek care"                     

PTam$neumoparazon_TxAthome <- factor(PTam$neumoparazon_TxAthome, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$neumoparazon_TxAthome, "label")<- "Prefer home treatment"

PTam$neumoparazon_Distrust <- factor(PTam$neumoparazon_Distrust, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$neumoparazon_Distrust, "label")<- "Distrust of healthcare services"

PTam$neumoparazon_Other <- factor(PTam$neumoparazon_Other, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$neumoparazon_Other, "label")<- "Other reason"


# For ILI, diarrhea, and FUO
#-----------------
PTam$buscoayudarazones_Nocreyoque1 <- factor(PTam$buscoayudarazones_Nocreyoque1, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$buscoayudarazones_Nocreyoque1, "label")<- "Did not think the illness was serious enough"

PTam$buscoayudarazones_Laclinicae2 <- factor(PTam$buscoayudarazones_Laclinicae2, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$buscoayudarazones_Laclinicae2, "label")<- "Healthcare facility was too far from home"

PTam$buscoayudarazones_Nohubomedi3 <- factor(PTam$buscoayudarazones_Nohubomedi3, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$buscoayudarazones_Nohubomedi3, "label")<- "No transportation was available"

PTam$buscoayudarazones_Noteniadin4 <- factor(PTam$buscoayudarazones_Noteniadin4, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$buscoayudarazones_Noteniadin4, "label")<- "Did not have enough money"

PTam$buscoayudarazones_Nopodiades5 <- factor(PTam$buscoayudarazones_Nopodiades5, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$buscoayudarazones_Nopodiades5, "label")<- "Could not leave household responsibilities"

PTam$buscoayudarazones_Nopodiaaus6 <- factor(PTam$buscoayudarazones_Nopodiaaus6, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$buscoayudarazones_Nopodiaaus6, "label")<- "Could not miss work"                     

PTam$buscoayudarazones_Nosabiaado7 <- factor(PTam$buscoayudarazones_Nosabiaado7, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$buscoayudarazones_Nosabiaado7, "label")<- "Did not know where to seek care"                     

PTam$buscoayudarazones_TxAthome <- factor(PTam$buscoayudarazones_TxAthome, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$buscoayudarazones_TxAthome, "label")<- "Prefer home treatment"

PTam$buscoayudarazones_NoMedicineClose <- factor(PTam$buscoayudarazones_NoMedicineClose, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$buscoayudarazones_NoMedicineClose, "label")<- "Healthcare facilities are closed or undersupplied"

PTam$buscoayudarazones_Distrust <- factor(PTam$buscoayudarazones_Distrust, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$buscoayudarazones_Distrust, "label")<- "Distrust of healthcare services"

PTam$buscoayudarazones_Other <- factor(PTam$buscoayudarazones_Other, levels = c(1,0), labels = c("Si", "No"))
attr(PTam$buscoayudarazones_Other, "label")<- "Other reason"

```



## + Other variables
```{r}
PTam$edad15 <- factor(PTam$edad15)
PTam$edad5 <- factor(PTam$edad5, 
                     levels = c("Menor5", "5oMas"),
                     labels = c("Menor5", "5oMas"),
                     ordered = 1)
PTam$COVID <- factor(PTam$COVID)


PTam$idiomahogar_des2 <- factor(ifelse(PTam$idiomahogar_des=="Spanish",1,0),
                                levels = c(1,0),
                                labels = c("Spanish", "Maya"))

PTam$edadcat <- factor(PTam$edadcat, 
                                levels=c("00-04", "05-14", "15-44", "45-64", ">=65"),
                                labels=c("00-04", "05-14", "15-44", "45-64", ">=65"),
                                ordered = T)
```


# 4. Table of recovered today

Pneumonia
```{r}
PTam |> filter(
  elegibleneumonia=="Si" &
  Period=="Before COVID - All ages" & 
  edad15 == "Menor15") |> 
  count(elegibleneumonia, enfermedadaun, neumopaayuda)


PTam |> filter(
  elegibleneumonia=="Si" &
  Period=="Before COVID - All ages" & 
  edad15 == "15oMas") |> 
  count(elegibleneumonia, enfermedadaun, neumopaayuda)


PTam |> filter(
  elegibleneumonia=="Si" &
  Period=="During COVID - <15 years") |> 
  count(elegibleneumonia, enfermedadaun, neumopaayuda)

```

ILI
```{r}
PTam |> filter(
  elegibleili=="Si" &
  Period=="Before COVID - All ages" & 
  edad15 == "Menor15") |> 
  count(elegibleili, enfermedadaun, buscoayuda)


PTam |> filter(
  elegibleili=="Si" &
  Period=="Before COVID - All ages" & 
  edad15 == "15oMas") |> 
  count(elegibleili, enfermedadaun, buscoayuda)


PTam |> filter(
  elegibleili=="Si" &
  Period=="During COVID - <15 years") |> 
  count(elegibleili, enfermedadaun, buscoayuda)

```


Diarrhea
```{r}
PTam |> filter(
  elegiblediarrea=="Si" &
  Period=="Before COVID - All ages" & 
  edad15 == "Menor15") |> 
  count(elegiblediarrea, enfermedadaun, buscoayuda)

PTam |> filter(
  elegiblediarrea=="Si" &
  Period=="Before COVID - All ages" & 
  edad15 == "15oMas") |> 
  count(elegiblediarrea, enfermedadaun, buscoayuda)

PTam |> filter(
  elegiblediarrea=="Si" &
  Period=="During COVID - <15 years") |> 
  count(elegiblediarrea, enfermedadaun, buscoayuda)
```


FUO
```{r}
PTam |> filter(
  elegiblefebril_FUO=="Si" &
  Period=="Before COVID - All ages" & 
  edad15 == "Menor15") |> 
  count(elegiblefebril_FUO, enfermedadaun, buscoayuda)

PTam |> filter(
  elegiblefebril_FUO=="Si" &
  Period=="Before COVID - All ages" & 
  edad15 == "15oMas") |> 
  count(elegiblefebril_FUO, enfermedadaun, buscoayuda)

PTam |> filter(
  elegiblefebril_FUO=="Si" &
  Period=="During COVID - <15 years") |> 
  count(elegiblefebril_FUO, enfermedadaun, buscoayuda)
```


# BEFORE COVID

# 5. Proportions

## + Pneumonia

```{r}
PTam %>% 
  filter(elegibleneumonia=="Si" & Period=="Before COVID - All ages") |> 
  count(Period, elegibleneumonia, enfermedadaun,  neumopaayuda)
```


Sought Healthcare
```{r}
data<-PTam %>% filter(elegibleneumonia=="Si" & Period =="Before COVID - All ages")
  
cg <-compareGroups(edad5 ~ neumopaayuda_des + 
                     PublicoPneumo_des + FarmaciaTiendaPneumo_des + TradicionalPneumo_des +
                     ClinicaPublicaPneumo_des + ClinicaPrivadaPneumo_des + 
                     ClinicaSeguroSocialPneumo_des + HospitalPublicaPneumo_des + HospitalPrivadoPneumo_des +
                     AntibioticoPneumo_des + AntibioticoPneumoSelf_des +
                     AntibioticoClasePneumo_des + BLactamPneumo_des + 
                     TetracyclinsPneumo_des + MacrolidesPneumo_des + LincosamidesPneumo_des +
                     AntibioticoCualPneumo_des,
                     data=data,
                     include.label = T)

dt<-createTable(cg, digits = 0, show.n = T, show.all = T)
print(dt, header.labels = c(all = "Prevalencias"), which.table = "both")
export2xls(dt, file= "output/Pneumonia_Proportions_BeforeCOVID_AllAges_ByAgeGroup.xlsx", header.labels = c(all = "Elegibles"), which.table = "both")
```


Reasons for not seeking healthcare:
```{r}
data<-PTam %>% filter(elegibleneumonia=="Si" & Period =="Before COVID - All ages" & neumopaayuda_des=="No")
cg <-compareGroups(edad5 ~ neumopaayuda_des + 
                     neumoparazon_Nocreyoque1 + neumoparazon_Laclinicae2 + 
                     neumoparazon_Nohubomedi3 + neumoparazon_Noteniadin4 + 
                     neumoparazon_Nopodiades5 + neumoparazon_Nopodiaaus6 + 
                     neumoparazon_Nosabiaado7 + neumoparazon_TxAthome + 
                     neumoparazon_Other + neumoparazon_Distrust,
                     data=data,
                     include.label = T)

dt<-createTable(cg, digits = 0, show.n = T, show.all = T)
print(dt, header.labels = c(all = "Prevalencias"), which.table = "both")
export2xls(dt, file= "output/Pneumonia_Reasons_BeforeCOVID_AllAges_ByAgeGroup.xlsx", header.labels = c(all = "Elegibles"), which.table = "both")
```



## + ILI

```{r}
PTam %>% 
  filter(elegibleili=="Si" & Period=="Before COVID - All ages") |> 
  count(Period, elegibleili, enfermedadaun,  buscoayuda)
```


Sought Healthcare:
```{r}
data<-PTam %>% filter(elegibleili=="Si" & Period =="Before COVID - All ages")

cg <-compareGroups(edad5 ~ buscoayuda_des + Publico_des +
                     FarmaciaTienda_des + Tradicional_des +
                     ClinicaPublica_des + ClinicaPrivada_des + 
                     ClinicaSeguroSocial_des + HospitalPublico_des + HospitalPrivado_des +
                     Antibiotico_des + AntibioticoSelf_des +
                     AntibioticoCual_des +AntibioticoClase_des +
                     BLactam_des + Tetracyclins_des + Macrolides_des + Lincosamides_des,
                     data=data,
                     include.label = T)

dt<-createTable(cg, digits = 0, show.n = T, show.all = T)
print(dt, header.labels = c(all = "Prevalencias"), which.table = "both")
export2xls(dt, file= "output/ILI_Proportions_BeforeCOVID_AllAges_ByAgeGroup.xlsx", 
           header.labels = c(all = "Elegibles"), which.table = "both")
```


Reasons for not seeking healthcare:
```{r}
data<-PTam %>% filter(elegibleili=="Si" & Period =="Before COVID - All ages" & buscoayuda_des=="No")

cg <-compareGroups(edad5 ~ buscoayuda_des + buscoayudarazones_Nocreyoque1 +
                     buscoayudarazones_Laclinicae2 + buscoayudarazones_Nohubomedi3 +
                     buscoayudarazones_Noteniadin4 + buscoayudarazones_Nopodiades5 +
                     buscoayudarazones_Nopodiaaus6 + buscoayudarazones_Nosabiaado7 +
                     buscoayudarazones_TxAthome + buscoayudarazones_NoMedicineClose +
                     buscoayudarazones_Distrust + buscoayudarazones_Other,
                     data=data,
                     include.label = T)

dt<-createTable(cg, digits = 0, show.n = T, show.all = T)
print(dt, header.labels = c(all = "Prevalencias"), which.table = "both")
export2xls(dt, file= "output/ILI_Reasons_BeforeCOVID_AllAges_ByAgeGroup.xlsx", header.labels = c(all = "Elegibles"), which.table = "both")
```


## + Diarrhea

```{r}
PTam %>% 
  filter(elegiblediarrea=="Si" & Period=="Before COVID - All ages") |> 
  count(Period, elegiblediarrea, enfermedadaun,  buscoayuda)
```

Sought Healthcare:
```{r}
data<-PTam %>% filter(elegiblediarrea=="Si" & Period =="Before COVID - All ages")

cg <-compareGroups(edad5 ~ buscoayuda_des + Publico_des +
                     FarmaciaTienda_des + Tradicional_des +
                     ClinicaPublica_des + ClinicaPrivada_des + 
                     ClinicaSeguroSocial_des + HospitalPublico_des + HospitalPrivado_des +
                     Antibiotico_des + AntibioticoSelf_des +
                     AntibioticoCual_des +AntibioticoClase_des +
                     BLactam_des + Tetracyclins_des + Macrolides_des + Lincosamides_des,
                     data=data,
                     include.label = T)

dt<-createTable(cg, digits = 0, show.n = T, show.all = T)
print(dt, header.labels = c(all = "Prevalencias"), which.table = "both")
export2xls(dt, file= "output/Diarrhea_Proportions_BeforeCOVID_AllAges_ByAgeGroup.xlsx", 
           header.labels = c(all = "Elegibles"), which.table = "both")


```

Reasons for not seeking healthcare:
```{r}
data<-PTam %>% filter(elegiblediarrea=="Si" & Period =="Before COVID - All ages" & buscoayuda_des=="No")

cg <-compareGroups(edad5 ~ buscoayuda_des +buscoayudarazones_Nocreyoque1 +
                     buscoayudarazones_Laclinicae2 + buscoayudarazones_Nohubomedi3 +
                     buscoayudarazones_Noteniadin4 + buscoayudarazones_Nopodiades5 +
                     buscoayudarazones_Nopodiaaus6 + buscoayudarazones_Nosabiaado7 +
                     buscoayudarazones_TxAthome + buscoayudarazones_NoMedicineClose +
                     buscoayudarazones_Distrust + buscoayudarazones_Other,
                     data=data,
                     include.label = T)

dt<-createTable(cg, digits = 0, show.n = T, show.all = T)
print(dt, header.labels = c(all = "Prevalencias"), which.table = "both")
export2xls(dt, file= "output/Diarrhea_Reasons_BeforeCOVID_AllAges_ByAgeGroup.xlsx", header.labels = c(all = "Elegibles"), which.table = "both")
```


## + FUO

```{r}
PTam %>% 
  filter(elegiblefebril_FUO=="Si" & Period=="Before COVID - All ages") |> 
  count(Period, elegiblefebril_FUO, enfermedadaun,  buscoayuda)
```



# 6. Ratios


## Declare survey


Aplicar la post estratificacion:
```{r}
PTam_S <- svydesign(id = ~cluster+id_record+IDPersona, 
                   data = PTam,
                   weights =  ~WeightCluster*WeightHouse*WeightInd)
PTam_S <-postStratify(PTam_S, strata = ~Strata, population = Censo)

PTam_S
```

## + Pneumonia

```{r}
PTam %>% filter(Period =="Before COVID - All ages" & elegibleneumonia_num==1 & enfermedadaun==0) %>% 
  count(elegibleneumonia_num)

subset <- subset(PTam_S, Period =="Before COVID - All ages" & elegibleneumonia_num==1 & enfermedadaun==0)

ratio<-svyratio(~neumopaayuda, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio1<-c(variable="SoughtHealthCare", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))
# check if is the same
svymean(~neumopaayuda, subset(PTam_S, Period =="Before COVID - All ages" & elegibleneumonia_num==1 & enfermedadaun==0), na.rm = TRUE)

ratio<-svyratio(~PublicoPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio2<-c(variable="AnyPublicFacility", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~FarmaciaTiendaPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio3<-c(variable="PharmacyCornerStore", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~TradicionalPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio4<-c(variable="TraditionalClinic", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~ClinicaPublicaPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio5<-c(variable="PublicClinic", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~ClinicaPrivadaPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio6<-c(variable="PrivateClinic", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~ClinicaSeguroSocialPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio7<-c(variable="SocialSecurityClinic", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~HospitalPublicaPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio8<-c(variable="PublicHospital", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~HospitalPrivadoPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio9<-c(variable="PrivateHospital",age="All ages",  estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~AntibioticoPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio10<-c(variable="Antibiotics", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~AntibioticoPneumoSelf, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio11<-c(variable="AntibioticsSelf", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~BLactamPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio12<-c(variable="BLactams", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~TetracyclinsPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio13<-c(variable="Tetracyclins", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~MacrolidesPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio14<-c(variable="Macrolides", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))
```


```{r}
PTam %>% filter(Period =="Before COVID - All ages" & elegibleneumonia_num==1 & enfermedadaun==0 & edad5=="Menor5") %>% 
  count(elegibleneumonia_num)

subset <- subset(PTam_S, Period =="Before COVID - All ages" & elegibleneumonia_num==1 & enfermedadaun==0 & edad5=="Menor5")

ratio<-svyratio(~neumopaayuda, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio15<-c(variable="SoughtHealthCare", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~PublicoPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio16<-c(variable="AnyPublicFacility", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~FarmaciaTiendaPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio17<-c(variable="PharmacyCornerStore", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~TradicionalPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio18<-c(variable="TraditionalClinic", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~ClinicaPublicaPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio19<-c(variable="PublicClinic", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~ClinicaPrivadaPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio20<-c(variable="PrivateClinic", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~ClinicaSeguroSocialPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio21<-c(variable="SocialSecurityClinic", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~HospitalPublicaPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio22<-c(variable="PublicHospital", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~HospitalPrivadoPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio23<-c(variable="PrivateHospital",age="0-4",  estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~AntibioticoPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio24<-c(variable="Antibiotics", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~AntibioticoPneumoSelf, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio25<-c(variable="AntibioticsSelf", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~BLactamPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio26<-c(variable="BLactams", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~TetracyclinsPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio27<-c(variable="Tetracyclins", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~MacrolidesPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio28<-c(variable="Macrolides", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))
```



```{r}
PTam %>% filter(Period =="Before COVID - All ages" & elegibleneumonia_num==1 & enfermedadaun==0 & edad5=="5oMas") %>% 
  count(elegibleneumonia_num)

subset <- subset(PTam_S, Period =="Before COVID - All ages" & elegibleneumonia_num==1 & enfermedadaun==0 & edad5=="5oMas")

ratio<-svyratio(~neumopaayuda, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio29<-c(variable="SoughtHealthCare", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~PublicoPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio30<-c(variable="AnyPublicFacility", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~FarmaciaTiendaPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio31<-c(variable="PharmacyCornerStore", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~TradicionalPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio32<-c(variable="TraditionalClinic", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~ClinicaPublicaPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio33<-c(variable="PublicClinic", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~ClinicaPrivadaPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio34<-c(variable="PrivateClinic", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~ClinicaSeguroSocialPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio35<-c(variable="SocialSecurityClinic", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~HospitalPublicaPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio36<-c(variable="PublicHospital", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~HospitalPrivadoPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio37<-c(variable="PrivateHospital",age=">=5",  estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~AntibioticoPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio38<-c(variable="Antibiotics", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~AntibioticoPneumoSelf, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio39<-c(variable="AntibioticsSelf", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~BLactamPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio40<-c(variable="BLactams", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~TetracyclinsPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio41<-c(variable="Tetracyclins", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~MacrolidesPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio42<-c(variable="Macrolides", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))
```


```{r}
Pneumo <- bind_rows(ratio1, ratio2, ratio3, ratio4, ratio5, ratio6,
                    ratio7, ratio8, ratio9, ratio10, ratio11, ratio12,
                    ratio13, ratio14, ratio15, ratio16, ratio17, ratio18,
                    ratio19, ratio20, ratio21, ratio22, ratio23, ratio24,
                    ratio25, ratio26, ratio27, ratio28, ratio29,
                    ratio30, ratio31, ratio32, ratio33, ratio34, ratio35,
                    ratio36, ratio37, ratio38, ratio39, ratio40, ratio41,
                    ratio42) |> 
  dplyr::rename("CI_Low"=CI1, "CI_High"=CI2)

Pneumo
writexl::write_xlsx(Pneumo, "output/Pneumonia_Ratios_BeforeCOVID_AllAges.xlsx")
```

## + ILI


```{r}
PTam %>% filter(Period =="Before COVID - All ages" & elegibleili_num==1 & enfermedadaun==0) %>% 
  count(elegibleili_num)

subset <- subset(PTam_S, Period =="Before COVID - All ages" & elegibleili_num==1 & enfermedadaun==0)

ratio<-svyratio(~buscoayuda, ~elegibleili_num, design=subset, na.rm=T)
ratio1<-c(variable="SoughtHealthCare", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Publico, ~elegibleili_num, design=subset, na.rm=T)
ratio2<-c(variable="AnyPublicFacility", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~FarmaciaTienda, ~elegibleili_num, design=subset, na.rm=T)
ratio3<-c(variable="PharmacyCornerStore", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Tradicional, ~elegibleili_num, design=subset, na.rm=T)
ratio4<-c(variable="TraditionalClinic", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~ClinicaPublica, ~elegibleili_num, design=subset, na.rm=T)
ratio5<-c(variable="PublicClinic", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~ClinicaPrivada, ~elegibleili_num, design=subset, na.rm=T)
ratio6<-c(variable="PrivateClinic", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~HospitalPublico, ~elegibleili_num, design=subset, na.rm=T)
ratio7<-c(variable="PublicHospital", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~HospitalPrivado, ~elegibleili_num, design=subset, na.rm=T)
ratio8<-c(variable="PrivateHospital", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Antibiotico, ~elegibleili_num, design=subset, na.rm=T)
ratio9<-c(variable="Antibiotic", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~AntibioticoSelf, ~elegibleili_num, design=subset, na.rm=T)
ratio10<-c(variable="AntibioticSelf", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~BLactam, ~elegibleili_num, design=subset, na.rm=T)
ratio11<-c(variable="BLactam", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Tetracyclins, ~elegibleili_num, design=subset, na.rm=T)
ratio12<-c(variable="Tetracyclins", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Sulfonamides, ~elegibleili_num, design=subset, na.rm=T)
ratio13<-c(variable="Sulfonamides", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Macrolides, ~elegibleili_num, design=subset, na.rm=T)
ratio14<-c(variable="Macrolides", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Lincosamides, ~elegibleili_num, design=subset, na.rm=T)
ratio15<-c(variable="Lincosamides", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))
```


```{r}
PTam %>% filter(Period =="Before COVID - All ages" & elegibleili_num==1 & enfermedadaun==0 & edad5=="Menor5") %>% 
  count(elegibleili_num)

subset <- subset(PTam_S, Period =="Before COVID - All ages" & elegibleili_num==1 & enfermedadaun==0 & edad5=="Menor5")

ratio<-svyratio(~buscoayuda, ~elegibleili_num, design=subset, na.rm=T)
ratio16<-c(variable="SoughtHealthCare", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Publico, ~elegibleili_num, design=subset, na.rm=T)
ratio17<-c(variable="AnyPublic", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~FarmaciaTienda, ~elegibleili_num, design=subset, na.rm=T)
ratio18<-c(variable="PharmacyCornerStore", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Tradicional, ~elegibleili_num, design=subset, na.rm=T)
ratio19<-c(variable="TraditionalClinic", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~ClinicaPublica, ~elegibleili_num, design=subset, na.rm=T)
ratio20<-c(variable="PublicClinic", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~ClinicaPrivada, ~elegibleili_num, design=subset, na.rm=T)
ratio21<-c(variable="PrivateClinic", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~HospitalPublico, ~elegibleili_num, design=subset, na.rm=T)
ratio22<-c(variable="PublicHospital", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~HospitalPrivado, ~elegibleili_num, design=subset, na.rm=T)
ratio23<-c(variable="PrivateHospital", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Antibiotico, ~elegibleili_num, design=subset, na.rm=T)
ratio24<-c(variable="Antibiotic", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~AntibioticoSelf, ~elegibleili_num, design=subset, na.rm=T)
ratio25<-c(variable="AntibioticSelf", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~BLactam, ~elegibleili_num, design=subset, na.rm=T)
ratio26<-c(variable="BLactam", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Tetracyclins, ~elegibleili_num, design=subset, na.rm=T)
ratio27<-c(variable="Tetracyclins", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Sulfonamides, ~elegibleili_num, design=subset, na.rm=T)
ratio28<-c(variable="Sulfonamides", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Macrolides, ~elegibleili_num, design=subset, na.rm=T)
ratio29<-c(variable="Macrolides", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))
```


```{r}
PTam %>% filter(Period =="Before COVID - All ages" & elegibleili_num==1 & enfermedadaun==0 & edad5=="5oMas") %>% 
  count(elegibleili_num)

subset <- subset(PTam_S, Period =="Before COVID - All ages" & elegibleili_num==1 & enfermedadaun==0 & edad5=="5oMas")

ratio<-svyratio(~buscoayuda, ~elegibleili_num, design=subset, na.rm=T)
ratio30<-c(variable="SoughtHealthCare", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Publico, ~elegibleili_num, design=subset, na.rm=T)
ratio31<-c(variable="AnyPublic", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~FarmaciaTienda, ~elegibleili_num, design=subset, na.rm=T)
ratio32<-c(variable="PharmacyCornerStore", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Tradicional, ~elegibleili_num, design=subset, na.rm=T)
ratio33<-c(variable="TraditionalClinic", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~ClinicaPublica, ~elegibleili_num, design=subset, na.rm=T)
ratio34<-c(variable="PublicClinic", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~ClinicaPrivada, ~elegibleili_num, design=subset, na.rm=T)
ratio35<-c(variable="PrivateClinic", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~HospitalPublico, ~elegibleili_num, design=subset, na.rm=T)
ratio36<-c(variable="PublicHospital", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~HospitalPrivado, ~elegibleili_num, design=subset, na.rm=T)
ratio37<-c(variable="PrivateHospital", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Antibiotico, ~elegibleili_num, design=subset, na.rm=T)
ratio38<-c(variable="Antibiotic", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~AntibioticoSelf, ~elegibleili_num, design=subset, na.rm=T)
ratio39<-c(variable="AntibioticSelf", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~BLactam, ~elegibleili_num, design=subset, na.rm=T)
ratio40<-c(variable="BLactam", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Tetracyclins, ~elegibleili_num, design=subset, na.rm=T)
ratio41<-c(variable="Tetracyclins", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Sulfonamides, ~elegibleili_num, design=subset, na.rm=T)
ratio42<-c(variable="Sulfonamides", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Macrolides, ~elegibleili_num, design=subset, na.rm=T)
ratio43<-c(variable="Macrolides", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))
```



```{r}
ILI <- bind_rows(ratio1, ratio2, ratio3, ratio4, ratio5, ratio6,
                    ratio7, ratio8, ratio9, ratio10, ratio11, ratio12,
                    ratio13, ratio14, ratio15, ratio16, ratio17, ratio18,
                    ratio19, ratio20, ratio21, ratio22, ratio23, ratio24,
                    ratio25, ratio26, ratio27, ratio28, ratio29,
                    ratio30, ratio31, ratio32, ratio33, ratio34, ratio35,
                    ratio36, ratio37, ratio38, ratio39, ratio40, ratio41,
                    ratio42, ratio43) |> 
  dplyr::rename("CI_Low"=CI1, "CI_High"=CI2)
ILI
writexl::write_xlsx(ILI, "output/ILI_Ratios_BeforeCOVID_AllAges.xlsx")
```




## + Diarrhea


```{r}
PTam %>% filter(Period =="Before COVID - All ages" & elegiblediarrea_num==1 & enfermedadaun==0) %>% 
  count(elegiblediarrea_num, buscoayuda, buscoayuda_des, HospitalPublico, HospitalPublico_des, HospitalPrivado, HospitalPrivado_des)

subset <- subset(PTam_S, Period =="Before COVID - All ages" & elegiblediarrea_num==1 & enfermedadaun==0)

ratio<-svyratio(~buscoayuda, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio1<-c(variable="SoughtHealthCare", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Publico, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio2<-c(variable="AnyPublic", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~FarmaciaTienda, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio3<-c(variable="PharmacyCornerStore", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Tradicional, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio4<-c(variable="TraditionalClinic", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~ClinicaPublica, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio5<-c(variable="PublicClinic", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~ClinicaPrivada, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio6<-c(variable="PrivateClinic", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~HospitalPublico, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio7<-c(variable="PublicHospital", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~HospitalPrivado, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio8<-c(variable="PrivateHospital", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Antibiotico, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio9<-c(variable="Antibiotic", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~AntibioticoSelf, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio10<-c(variable="AntibioticSelf", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~BLactam, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio11<-c(variable="BLactam", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Tetracyclins, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio12<-c(variable="Tetracyclins", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Sulfonamides, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio13<-c(variable="Sulfonamides", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Macrolides, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio14<-c(variable="Macrolides", age="All ages", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))
```


```{r}
PTam %>% filter(Period =="Before COVID - All ages" & elegiblediarrea_num==1 & enfermedadaun==0 & edad5=="Menor5") %>% 
  count(elegiblediarrea_num)

subset <- subset(PTam_S, Period =="Before COVID - All ages" & elegiblediarrea_num==1 & enfermedadaun==0 & edad5=="Menor5")

ratio<-svyratio(~buscoayuda, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio15<-c(variable="SoughtHealthCare", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Publico, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio16<-c(variable="AnyPublic", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~FarmaciaTienda, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio17<-c(variable="PharmacyCornerStore", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Tradicional, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio18<-c(variable="TraditionalClinic", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~ClinicaPublica, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio19<-c(variable="PublicClinic", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~ClinicaPrivada, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio20<-c(variable="PrivateClinic", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~HospitalPublico, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio21<-c(variable="PublicHospital", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~HospitalPrivado, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio22<-c(variable="PrivateHospital", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Antibiotico, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio23<-c(variable="Antibiotic", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~AntibioticoSelf, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio24<-c(variable="AntibioticSelf", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~BLactam, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio25<-c(variable="BLactam", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Tetracyclins, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio26<-c(variable="Tetracyclins", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Sulfonamides, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio27<-c(variable="Sulfonamides", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Macrolides, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio28<-c(variable="Macrolides", age="0-4", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))
```

```{r}
PTam %>% filter(Period =="Before COVID - All ages" & elegiblediarrea_num==1 & enfermedadaun==0 & edad5=="5oMas") %>% 
  count(elegiblediarrea_num)

subset <- subset(PTam_S, Period =="Before COVID - All ages" & elegiblediarrea_num==1 & enfermedadaun==0 & edad5=="5oMas")

ratio<-svyratio(~buscoayuda, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio29<-c(variable="SoughtHealthCare", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Publico, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio30<-c(variable="AnyPublic", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~FarmaciaTienda, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio31<-c(variable="PharmacyCornerStore", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Tradicional, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio32<-c(variable="TraditionalClinic", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~ClinicaPublica, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio33<-c(variable="PublicClinic", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~ClinicaPrivada, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio34<-c(variable="PrivateClinic", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~HospitalPublico, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio35<-c(variable="PublicHospital", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~HospitalPrivado, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio36<-c(variable="PrivateHospital", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Antibiotico, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio37<-c(variable="Antibiotic", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~AntibioticoSelf, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio38<-c(variable="AntibioticSelf", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~BLactam, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio39<-c(variable="BLactam", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Tetracyclins, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio40<-c(variable="Tetracyclins", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Sulfonamides, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio41<-c(variable="Sulfonamides", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Macrolides, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio42<-c(variable="Macrolides", age=">=5", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))
```



```{r}
Diarhea <- bind_rows(ratio1, ratio2, ratio3, ratio4, ratio5, ratio6,
                    ratio7, ratio8, ratio9, ratio10, ratio11, ratio12,
                    ratio13, ratio14, ratio15, ratio16, ratio17, ratio18,
                    ratio19, ratio20, ratio21, ratio22, ratio23, ratio24,
                    ratio25, ratio26, ratio27, ratio28, ratio29,
                    ratio30, ratio31, ratio32, ratio33, ratio34, ratio35,
                    ratio36, ratio37, ratio38, ratio39, ratio40, ratio41,
                    ratio42, ratio43) |> 
  dplyr::rename("CI_Low"=CI1, "CI_High"=CI2)

Diarhea
writexl::write_xlsx(ILI, "output/Diarhea_Ratios_BeforeCOVID_AllAges.xlsx")
```



## BEFORE & AFTER

# 7. Proportions

## + Pneumonia

Place of healthcare seeking:
```{r}
data<-PTam %>% filter(elegibleneumonia=="Si" & Period !="During COVID - All ages" & edad15=="Menor15")

cg <-compareGroups(Period ~ neumopaayuda_des + PublicoPneumo_des +
                     FarmaciaTiendaPneumo_des + TradicionalPneumo_des +
                     ClinicaPublicaPneumo_des + ClinicaPrivadaPneumo_des + 
                     ClinicaSeguroSocialPneumo_des + HospitalPublicaPneumo_des + HospitalPrivadoPneumo_des +
                     AntibioticoPneumo_des + AntibioticoPneumoSelf_des +
                     AntibioticoClasePneumo_des + AntibioticoCualPenumo_des +
                     BLactamPneumo_des + 
                     TetracyclinsPneumo_des + MacrolidesPneumo_des + LincosamidesPneumo_des,
                     data=data,
                     include.label = T)

dt<-createTable(cg, digits = 0, show.n = T, show.all = T)
print(dt, header.labels = c(all = "Prevalencias"), which.table = "both")
export2xls(dt, file= "output/Pneumonia_Proportions_BeforeDuringCOVID_Children_ByPeriod.xlsx", header.labels = c(all = "Elegibles"), which.table = "both")
```


Reasons for not seeking care
```{r}
data<-PTam %>% filter(elegibleneumonia=="Si" & Period !="During COVID - All ages" & edad15=="Menor15" & neumopaayuda_des=="No")

cg <-compareGroups(Period ~  neumoparazon_Nocreyoque1 + neumoparazon_Laclinicae2 + 
                     neumoparazon_Nohubomedi3 + neumoparazon_Noteniadin4 + 
                     neumoparazon_Nopodiades5 + neumoparazon_Nopodiaaus6 + 
                     neumoparazon_Nosabiaado7 + neumoparazon_TxAthome + 
                     neumoparazon_Other + neumoparazon_Distrust,
                     data=data,
                     include.label = T)

dt<-createTable(cg, digits = 0, show.n = T, show.all = T)
print(dt, header.labels = c(all = "Prevalencias"), which.table = "both")
export2xls(dt, file= "output/Pneumonia_Reasons_BeforeDuringCOVID_Children_ByPeriod.xlsx", header.labels = c(all = "Elegibles"), which.table = "both")
```







## + ILI

Place of healthcare seeking:
```{r}
data<-PTam %>% filter(elegibleili=="Si" & Period !="During COVID - All ages" & edad15=="Menor15")

cg <-compareGroups(Period ~ buscoayuda_des + Publico_des +
                     FarmaciaTienda_des + Tradicional_des +
                     ClinicaPublica_des + ClinicaPrivada_des + 
                     ClinicaSeguroSocial_des + HospitalPublico_des + HospitalPrivado_des +
                     Antibiotico_des + AntibioticoSelf_des +
                     AntibioticoCual_des +AntibioticoClase_des +
                     BLactam_des + Tetracyclins_des + Macrolides_des + Lincosamides_des,
                     data=data,
                     include.label = T)

dt<-createTable(cg, digits = 0, show.n = T, show.all = T)
print(dt, header.labels = c(all = "Prevalencias"), which.table = "both")
export2xls(dt, file= "output/ILI_Proportions_BeforeDuringCOVID_Children_ByPeriod.xlsx", header.labels = c(all = "Elegibles"), which.table = "both")
```



Reasons for not seeking care
```{r}
data<-PTam %>% filter(elegibleili=="Si" & Period !="During COVID - All ages" & edad15=="Menor15" & buscoayuda_des=="No")

cg <-compareGroups(Period ~ buscoayudarazones_Nocreyoque1 +
                     buscoayudarazones_Laclinicae2 + buscoayudarazones_Nohubomedi3 +
                     buscoayudarazones_Noteniadin4 + buscoayudarazones_Nopodiades5 +
                     buscoayudarazones_Nopodiaaus6 + buscoayudarazones_Nosabiaado7 +
                     buscoayudarazones_TxAthome + buscoayudarazones_NoMedicineClose +
                     buscoayudarazones_Distrust + buscoayudarazones_Other,
                     data=data,
                     include.label = T)

dt<-createTable(cg, digits = 0, show.n = T, show.all = T)
print(dt, header.labels = c(all = "Prevalencias"), which.table = "both")
export2xls(dt, file= "output/ILI_Reasons_BeforeDuringCOVID_Children_ByPeriod.xlsx", header.labels = c(all = "Elegibles"), which.table = "both")
```

## + Diarrea
```{r}
data<-PTam %>% filter(elegiblediarrea=="Si" & Period !="During COVID - All ages" & edad15=="Menor15")

cg <-compareGroups(Period ~ buscoayuda_des + Publico_des +
                     FarmaciaTienda_des + Tradicional_des +
                     ClinicaPublica_des + ClinicaPrivada_des + 
                     ClinicaSeguroSocial_des + HospitalPublico_des + HospitalPrivado_des +
                     Antibiotico_des + AntibioticoSelf_des +
                     AntibioticoCual_des +AntibioticoClase_des +
                     BLactam_des + Tetracyclins_des + Macrolides_des + Lincosamides_des,
                     data=data,
                     include.label = T)

dt<-createTable(cg, digits = 0, show.n = T, show.all = T)
print(dt, header.labels = c(all = "Prevalencias"), which.table = "both")
export2xls(dt, file= "output/Diarrhea_Proportions_BeforeDuringCOVID_Children_ByPeriod.xlsx", header.labels = c(all = "Elegibles"), which.table = "both")
```

Reasons for not seeking care:
```{r}
data<-PTam %>% filter(elegiblediarrea=="Si" & Period !="During COVID - All ages" & edad15=="Menor15" & buscoayuda_des=="No")

cg <-compareGroups(Period ~ buscoayudarazones_Nocreyoque1 +
                     buscoayudarazones_Laclinicae2 + buscoayudarazones_Nohubomedi3 +
                     buscoayudarazones_Noteniadin4 + buscoayudarazones_Nopodiades5 +
                     buscoayudarazones_Nopodiaaus6 + buscoayudarazones_Nosabiaado7 +
                     buscoayudarazones_TxAthome + buscoayudarazones_NoMedicineClose +
                     buscoayudarazones_Distrust + buscoayudarazones_Other,
                     data=data,
                     include.label = T)

dt<-createTable(cg, digits = 0, show.n = T, show.all = T)
print(dt, header.labels = c(all = "Prevalencias"), which.table = "both")
export2xls(dt, file= "output/Diarrhea_Reasons_BeforeDuringCOVID_Children_ByPeriod.xlsx", header.labels = c(all = "Elegibles"), which.table = "both")
```




# 8. Ratios


## Declare survey


Aplicar la post estratificacion:
```{r}
PTam_S <- svydesign(id = ~cluster+id_record+IDPersona, 
                   data = PTam,
                   weights =  ~WeightCluster*WeightHouse*WeightInd)
PTam_S <-postStratify(PTam_S, strata = ~Strata, population = Censo)

PTam_S
```


## + Pneumonia

```{r}
PTam %>% filter(edad15=="Menor15", Period =="Before COVID - All ages" & elegibleneumonia_num==1 & enfermedadaun==0) %>% 
  count(elegibleneumonia_num)

subset <- subset( PTam_S, edad15=="Menor15" & Period =="Before COVID - All ages" & elegibleneumonia_num==1 & enfermedadaun==0)

ratio<-svyratio(~neumopaayuda, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio1<-c(variable="SoughtHealthCare", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~PublicoPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio2<-c(variable="AnyPublic", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~FarmaciaTiendaPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio3<-c(variable="PharmacyCornerStore", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~TradicionalPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio4<-c(variable="TraditionalClinic", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~ClinicaPublicaPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio5<-c(variable="PublicClinic", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~ClinicaPrivadaPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio6<-c(variable="PrivateClinic", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~HospitalPublicaPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio7<-c(variable="PublicHospital", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~HospitalPrivadoPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio8<-c(variable="PrivateHospital", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~AntibioticoPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio9<-c(variable="Antibiotic", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~AntibioticoPneumoSelf, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio10<-c(variable="AntibioticSelf", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~BLactamPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio11<-c(variable="BLacta,", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~TetracyclinsPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio12<-c(variable="Tetracyclins", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~MacrolidesPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio13<-c(variable="Macrolides", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))
```
```{r}
PTam %>% filter(edad15=="Menor15", Period =="During COVID - <15 years" & elegibleneumonia_num==1 & enfermedadaun==0) %>% 
  count(elegibleneumonia_num)

subset <- subset( PTam_S, edad15=="Menor15" & Period =="During COVID - <15 years" & elegibleneumonia_num==1 & enfermedadaun==0)

ratio<-svyratio(~neumopaayuda, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio14<-c(variable="SoughtHealthCare", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~PublicoPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio15<-c(variable="AnyPublic", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~FarmaciaTiendaPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio16<-c(variable="PharmacyCornerStore", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~TradicionalPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio17<-c(variable="TraditionalClinic", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~ClinicaPublicaPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio18<-c(variable="PublicClinic", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~ClinicaPrivadaPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio19<-c(variable="PrivateClinic", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~ClinicaSeguroSocialPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio20<-c(variable="SocialSecurityClinic", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~HospitalPublicaPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio21<-c(variable="PublicHospital", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~HospitalPrivadoPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio22<-c(variable="PrivateHospital", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~AntibioticoPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio23<-c(variable="Antibiotic", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~AntibioticoPneumoSelf, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio24<-c(variable="AntibioticSelf", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~BLactamPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio25<-c(variable="BLactam", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~TetracyclinsPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio26<-c(variable="Tetracyclins", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~MacrolidesPneumo, ~elegibleneumonia_num, design=subset, na.rm=T)
ratio27<-c(variable="Macrolides", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))
```



```{r}
Pneumo <- bind_rows(ratio1, ratio2, ratio3, ratio4, ratio5, ratio6,
                    ratio7, ratio8, ratio9, ratio10, ratio11, ratio12,
                    ratio13, ratio14, ratio15, ratio16, ratio17, ratio18,
                    ratio19, ratio20, ratio21, ratio22, ratio23, ratio24,
                    ratio25, ratio26, ratio27) |> 
  dplyr::rename("CI_Low"=CI1, "CI_High"=CI2)

Pneumo
writexl::write_xlsx(Pneumo, "output/Pneumonia_Ratios_BeforeDuringCOVID_Children.xlsx")
```



## + ILI

```{r}
PTam %>% filter(edad15=="Menor15", Period =="Before COVID - All ages" & elegibleili_num==1 & enfermedadaun==0) %>% 
  count(elegibleili_num)

subset <- subset( PTam_S, edad15=="Menor15" & Period =="Before COVID - All ages" & elegibleili_num==1 & enfermedadaun==0)

ratio<-svyratio(~buscoayuda, ~elegibleili_num, design=subset, na.rm=T)
ratio1<-c(variable="SoughtHealthCare", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Publico, ~elegibleili_num, design=subset, na.rm=T)
ratio2<-c(variable="AnyPublic", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~FarmaciaTienda, ~elegibleili_num, design=subset, na.rm=T)
ratio3<-c(variable="PharmacyCornerStore", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Tradicional, ~elegibleili_num, design=subset, na.rm=T)
ratio4<-c(variable="TraditionalClinic", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~ClinicaPublica, ~elegibleili_num, design=subset, na.rm=T)
ratio5<-c(variable="PublicClinic", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~ClinicaPrivada, ~elegibleili_num, design=subset, na.rm=T)
ratio6<-c(variable="PrivateClinic", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~HospitalPublico, ~elegibleili_num, design=subset, na.rm=T)
ratio7<-c(variable="PublicHospital", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~HospitalPrivado, ~elegibleili_num, design=subset, na.rm=T)
ratio8<-c(variable="PrivateHospital", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Antibiotico, ~elegibleili_num, design=subset, na.rm=T)
ratio9<-c(variable="Antibiotic", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~AntibioticoSelf, ~elegibleili_num, design=subset, na.rm=T)
ratio10<-c(variable="AntibioticSelf", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~BLactam, ~elegibleili_num, design=subset, na.rm=T)
ratio11<-c(variable="BLactam", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Tetracyclins, ~elegibleili_num, design=subset, na.rm=T)
ratio12<-c(variable="Tetracyclins", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Sulfonamides, ~elegibleili_num, design=subset, na.rm=T)
ratio13<-c(variable="Sulfonamides", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Macrolides, ~elegibleili_num, design=subset, na.rm=T)
ratio14<-c(variable="SoughtHealthCare", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))
```




```{r}
PTam %>% filter(edad15=="Menor15", Period =="During COVID - <15 years" & elegibleili_num==1 & enfermedadaun==0) %>% 
  count(elegibleili_num)

subset <- subset( PTam_S, edad15=="Menor15" & Period =="During COVID - <15 years" & elegibleili_num==1 & enfermedadaun==0)

ratio<-svyratio(~buscoayuda, ~elegibleili_num, design=subset, na.rm=T)
ratio15<-c(variable="SoughtHealthCare", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Publico, ~elegibleili_num, design=subset, na.rm=T)
ratio16<-c(variable="AnyPublic", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~FarmaciaTienda, ~elegibleili_num, design=subset, na.rm=T)
ratio17<-c(variable="PharmacyCornerStore", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Tradicional, ~elegibleili_num, design=subset, na.rm=T)
ratio18<-c(variable="TraditionalClinic", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~ClinicaPublica, ~elegibleili_num, design=subset, na.rm=T)
ratio19<-c(variable="PublicClinic", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~ClinicaPrivada, ~elegibleili_num, design=subset, na.rm=T)
ratio20<-c(variable="PrivateClinic", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~ClinicaSeguroSocial, ~elegibleili_num, design=subset, na.rm=T)
ratio21<-c(variable="SocialSecurityClinic", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~HospitalPublico, ~elegibleili_num, design=subset, na.rm=T)
ratio22<-c(variable="PublicHospital", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~HospitalPrivado, ~elegibleili_num, design=subset, na.rm=T)
ratio23<-c(variable="PrivateHospital", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Antibiotico, ~elegibleili_num, design=subset, na.rm=T)
ratio24<-c(variable="Antibiotic", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~AntibioticoSelf, ~elegibleili_num, design=subset, na.rm=T)
ratio25<-c(variable="AntibioticSelf", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~BLactam, ~elegibleili_num, design=subset, na.rm=T)
ratio26<-c(variable="BLactams", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Tetracyclins, ~elegibleili_num, design=subset, na.rm=T)
ratio27<-c(variable="Tetracyclins", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Sulfonamides, ~elegibleili_num, design=subset, na.rm=T)
ratio28<-c(variable="Sulfonamides", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Macrolides, ~elegibleili_num, design=subset, na.rm=T)
ratio29<-c(variable="Macrolides", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))
```


```{r}
ILI <- bind_rows(ratio1, ratio2, ratio3, ratio4, ratio5, ratio6,
                    ratio7, ratio8, ratio9, ratio10, ratio11, ratio12,
                    ratio13, ratio14, ratio15, ratio16, ratio17, ratio18,
                    ratio19, ratio20, ratio21, ratio22, ratio23, ratio24,
                    ratio25, ratio26, ratio27, ratio28, ratio29) |> 
  dplyr::rename("CI_Low"=CI1, "CI_High"=CI2)

ILI
writexl::write_xlsx(ILI, "output/ILI_Ratios_BeforeDuringCOVID_Children.xlsx")
```



## + Diarrhea

```{r}
PTam %>% filter(edad15=="Menor15", Period =="Before COVID - All ages" & elegiblediarrea=="Si" & enfermedadaun==0) %>%   count(elegiblediarrea)

subset <- subset( PTam_S, edad15=="Menor15" & Period =="Before COVID - All ages" & elegiblediarrea_num==1 & enfermedadaun==0)

ratio<-svyratio(~buscoayuda, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio1<-c(variable="SoughtHealthCare", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Publico, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio2<-c(variable="AnyPublic", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~FarmaciaTienda, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio3<-c(variable="PharmacyCornerStore", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Tradicional, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio4<-c(variable="TraditionalClinic", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~ClinicaPublica, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio5<-c(variable="PublicClinic", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~ClinicaPrivada, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio6<-c(variable="PrivateClinic", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~HospitalPublico, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio7<-c(variable="PublicHospital", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~HospitalPrivado, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio8<-c(variable="PrivateHospital", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Antibiotico, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio9<-c(variable="Antibiotic", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~AntibioticoSelf, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio10<-c(variable="AntibioticSelf", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~BLactam, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio11<-c(variable="BLactam", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Tetracyclins, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio12<-c(variable="Tetracyclins", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Sulfonamides, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio13<-c(variable="Sulfonamides", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Macrolides, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio14<-c(variable="Macrolides", age="<15 years", Period="Before COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))
```

```{r}
PTam %>% filter(edad15=="Menor15", Period =="During COVID - <15 years" & elegiblediarrea_num==1 & enfermedadaun==0) %>% 
  count(elegiblediarrea_num, AntibioticoClase_des, BLactam, Tetracyclins)

subset <- subset(PTam_S, edad15=="Menor15" & Period =="During COVID - <15 years" & elegiblediarrea_num==1 & enfermedadaun==0)

ratio<-svyratio(~buscoayuda, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio15<-c(variable="SoughtHealthCare", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Publico, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio16<-c(variable="AnyPublic", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~FarmaciaTienda, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio17<-c(variable="PharmacyCornerStore", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Tradicional, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio18<-c(variable="TraditionalClinic", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~ClinicaPublica, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio19<-c(variable="PublicClinic", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~ClinicaPrivada, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio20<-c(variable="PrivateClinic", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~ClinicaSeguroSocial, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio21<-c(variable="SocialSecurityClinic", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~HospitalPublico, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio22<-c(variable="PublicHospital", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~HospitalPrivado, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio23<-c(variable="PrivateHospital", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Antibiotico, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio24<-c(variable="Antibiotic", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~AntibioticoSelf, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio25<-c(variable="AntibioticSelf", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~BLactam, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio26<-c(variable="BLactam", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Tetracyclins, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio27<-c(variable="Tetracyclins", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Sulfonamides, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio28<-c(variable="Sulfonamides", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Macrolides, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio29<-c(variable="Macrolides", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))

ratio<-svyratio(~Nitroimidazoles, ~elegiblediarrea_num, design=subset, na.rm=T)
ratio30<-c(variable="Nitroimidazoles", age="<15 years", Period="During COVID", estimate=round(ratio$ratio*100), CI=round(confint(ratio)*100))
```


```{r}
Diarrhea <- bind_rows(ratio1, ratio2, ratio3, ratio4, ratio5, ratio6,
                    ratio7, ratio8, ratio9, ratio10, ratio11, ratio12,
                    ratio13, ratio14, ratio15, ratio16, ratio17, ratio18,
                    ratio19, ratio20, ratio21, ratio22, ratio23, ratio24,
                    ratio25, ratio26, ratio27, ratio28, ratio29, ratio30) |> 
  dplyr::rename("CI_Low"=CI1, "CI_High"=CI2)

Diarrhea
writexl::write_xlsx(Diarrhea, "output/Diarrhea_Ratios_BeforeDuringCOVID_Children.xlsx")
```


## FIN

