---
title: "Description of participants"
author: "Laura Grajeda"
date: "12 de mayo de 2020"
output: html_document
---


```{r}
library(tidyverse)
library(sf)
library(here)
library(compareGroups)
```


# 1. Aim

Describe participants included in the HUS analysis.

- Create a map of the distribution of the clusters
- Describe demographic characteristics of the households and individuals


# 2. Datos

## Tamizados

```{r}
PTam <- readRDS(here("1_Create_dataset", "output", "HUS_Dataset.rds"))
```


Filter to the period of interest. Exclude During-COVID - 
```{r}
PTam <- PTam %>% filter(Period == "Before COVID - All ages" | Period == "During COVID - <15 years")
```


## Shapefiles

Shape del departmaneto
```{r}
my_shapefile <- st_read(here("2_Participants_Description/input/gadm41_GTM_shp/gadm41_GTM_2.shp"))
my_shapefile <- my_shapefile %>% filter(NAME_1=="Quezaltenango")
```



# 3. General description

Number of clusters, households, and persons per period

Pre COVID
```{r}
PTam %>% filter(Period == "Before COVID - All ages") %>% 
  count(cluster)

PTam %>% filter(Period == "Before COVID - All ages") %>% 
  count(id_record)
  
PTam %>% filter(Period == "Before COVID - All ages") %>% 
  count(IDPersona)
```

During COVID
```{r}
PTam %>% filter(Period == "During COVID - <15 years") %>% 
  count(cluster)

PTam %>% filter(Period == "During COVID - <15 years") %>% 
  count(id_record)
  
PTam %>% filter(Period == "During COVID - <15 years") %>% 
  count(IDPersona)
```


# 4. Clusters


Municipios
```{r}
table(PTam$municipio_des, PTam$COVID)
```




Mapa

Ver datos. Hay clusters que comparten el mismo centroide.
```{r}
PTam %>% distinct(cluster, .keep_all = T) %>% 
  count(xCent, yCent) %>% 
  arrange(desc(n))

# -91.62949, 14.86047, n=4: 2 en Concepcion chiquirichapa y 2 en San Juan ostuncalco
PTam %>% 
  distinct(cluster, .keep_all = T) %>% 
  select(cluster, xCent, yCent, municipio_des) %>% arrange(xCent)
```


```{r}
PTam <- PTam %>% 
  mutate(Phase = case_when(
    COVID=="Before" ~ "Nov 2019-Mar 2020",
    COVID=="During" ~ "Oct 2021-May 2022"))
```



Plot
```{r}
p<-ggplot() +
  geom_sf(data = my_shapefile) +
  geom_jitter(data = PTam, aes(x=xCent, y=yCent, color=Phase), width = 0.005, height = 0.005, alpha=0.5)+
  geom_point(aes(x=-91.539882, y=14.860765, shape=""), size = 3, colour = "black", fill = "black") +
  labs(shape="Hospital:", color="Study phase:")+
  theme(legend.position = "bottom") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

```{r}
ggsave("output/map.png")
```


# 5. Hogares


Household questionnaire was incomplete for: A044-009-02, A147-010-02, A388-013-03


Language
```{r}
PTam$idiomahogar_des <- factor(PTam$idiomahogar_des)
```



Crowding
```{r}
PTam %>% count(numPer, casaespaciosdormir, hacinamiento, hacinamiento_cat)

PTam$hacinamiento_cat <- factor(PTam$hacinamiento_cat, 
                                levels = c("<=2","(2, 3]",">3"), labels = c("<=2", "(2, 3]", ">3"))

PTam %>% count(hacinamiento_cat)
```


Combustible
```{r}
PTam %>% count(combustiblecocinaprincipal_cal)

PTam$combustiblecocinaprincipal_cal <- factor(PTam$combustiblecocinaprincipal_cal)

```


Fuente de agua
```{r}
PTam %>% count(fuenteagua_cal)
PTam$fuenteagua_cal <- factor(PTam$fuenteagua_cal)
```



# 6. Individuos

Edad
```{r}
PTam %>% count(edadcat)
```

Sexo
```{r}
PTam %>% count(sexo_des)
```

Educacion
```{r}
# En ensmi esta pregunta de educacion solo se reporte para los mayores de 6 anos
PTam %>% count(educacion_cal)

PTam <- PTam %>% 
  mutate(educacion_cal = factor(case_when(
    edadnum<6 ~ NA_character_,
    TRUE ~ educacion_cal)))
```
Sanitario
```{r}
PTam %>% count(sanitario_cal)
```


# 7. Comparison

## By COVID

```{r}
cg1 <-compareGroups(COVID ~ area_des + municipio_des,
                  data=PTam,
                  include.label = T,
                  include.miss = TRUE)

cg2 <-compareGroups(COVID ~ idiomahogar_des + hacinamiento_cat + 
                  combustiblecocinaprincipal_cal + fuenteagua_cal + sanitario_cal +
                    SES_Tertiles,
                  data=PTam,
                  include.label = T,
                  include.miss = TRUE)

cg3 <-compareGroups(COVID ~ edadcat + sexo_des + educacion_cal,
                  data=PTam,
                  include.label = T,
                  include.miss = TRUE)


cg<-rbind(`Clusters` = cg1,
          `Hogares` = cg2,
          `Individuos` = cg3)

dt<-createTable(cg, digits = 0, show.n = T, show.all = T)
print(dt, which.table = "both")
export2xls(dt, file= "output/Participant characteristics by COVID period.xlsx", which.table = "both")
```

## By COVID restricted to <15

```{r}
cg1 <-compareGroups(COVID ~ area_des + municipio_des,
                  data=PTam %>% filter(edad15=="Menor15"),
                  include.label = T)

cg2 <-compareGroups(COVID ~ idiomahogar_des + hacinamiento_cat + 
                  combustiblecocinaprincipal_cal + fuenteagua_cal + sanitario_cal + SES_Tertiles,
                  data=PTam %>% filter(edad15=="Menor15"),
                  include.label = T)

cg3 <-compareGroups(COVID ~ edadcat + sexo_des + educacion_cal,
                  data=PTam %>% filter(edad15=="Menor15"),
                  include.label = T)


cg<-rbind(`Clusters` = cg1,
          `Hogares` = cg2,
          `Individuos` = cg3)

dt<-createTable(cg, digits = 0, show.n = T, show.all = T)
print(dt, which.table = "both")
export2xls(dt, file= "output/Participant characteristics by COVID period and restricted to younger than 15 yeras.xlsx", which.table = "both")
```



THE END








